---
title: "Coral Holobiont Physiology under ramping temperature exposure"
output: 
  html_document:
    theme: simplex
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

<style>
  h2{color: teal !important}
  h1{color: navy !important}
  body{background-color: gray95 !important}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(warn = -1)
```

```{r packages, include=FALSE}
setwd("C:/Github/TPC_Acropora")
#library("devtools")
#install_github("vqv/ggbiplot") # need this to download ggbiplot if not already installed
## Packages to load
library(devtools)
#install_github("vqv/ggbiplot")
#library(ggbiplot)
#require(devtools)
library(usethis)
#library(install_version)
library(magrittr)
#install_version("Magritter", version = "	2.0.1", repos = "http://cran.us.r-project.org")
library(knitr)
library(readr)
library(ggplot2)
library(dplyr)
#library(ggbiplot)
library(tidyr)
#library(openxlsx)
library(plotly)
library(tidyverse)
library(vegan)
library(shiny)
library(Rmisc)
library(cowplot)
library(ggfortify)
library(kableExtra)
library(readr)
#library(lmerTest)
library(vroom)
library(ggpubr)
library(magick)
library(Hmisc)
library(corrplot)
library(grid)
library(gridGraphics)
library(performance)
library(MASS)
library(r2symbols)
library(corrgram)
library(factoextra)
library(FactoMineR)

```

```{r set formatting and labels, include=FALSE}
## Set some standards and units
# dodge width
dodge=position_dodge(width=0.3)
dodge2=position_dodge(width = 0.6)
jitter=position_jitter(width=0.1)
# set figure theme
theme_set(theme_classic())
# set parameter labels
Plab<-expression(paste("log ", mu,"mol cm"^{-2}, "hr"^{-1}))
Tlab<-"Temperature (°C)"
plab<-expression(paste("Total protein ( "*mu,"g cm"^-2,")"))
dlab<-expression(paste("Cell density (10"^5,"cells cm"^-2,")"))
glab<-expression(paste("Growth Rate (%)"))
clab<-expression(paste("Chlorophyll a ( "*mu,"g cm"^-2,")"))
# set the current date
date <- Sys.Date() 
```

```{r original dataframe adjustment, include=FALSE}
df <- read_csv("C:/Github/TPC_Acropora/R_output_Data_Frames/EcophysLOGGEDdata.csv")
View(df)
# read in full dataframe
# remove unnecessary column
df$X1 <- NULL
# set columns as factors
df$cat <- as.factor(df$cat)
df$genotype <- as.factor(df$genotype)
df$coral_id <- as.factor(df$coral_id)
df$treatment <- as.factor(df$treatment) 
# rename a couple columns
names(df)[15]<-"Chlo"
names(df)[19]<-"Growth"
names(df)[5]<-"Pro"
names(df)[23]<-"Zoox" 

# select columns of interest only
df2 <- df[,c(1:3,5,15, 19,22, 23)] 

#data.table::setnames(df2, old = c('protein_3d_ug_cm2','chl_ug_cm2', 'percent_growth', 'totzoox'), new = c('pro','chlo','growth', 'zoox')) #rename for plotting

df2 <- gather(df2, param, value, 'Pro','Chlo','Growth', 'Zoox') # make column of parameter and value

```

```{r bootstrap model setup}
## Performing the parametric bootstrapping of the model:
bootnum = 1500 # set number of iterations (we used 2000) between 999 and 9999
seed = 7 # seed to make results replicatable (our seed was 3)
set.seed(7)
```


```{r}
df_s <- df[,c(1:3,5,15, 19,22, 23)] 

## Function to remove rows with any missing values
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}



df_s <- completeFun(df_s, "Chlo")
df_s <- completeFun(df_s, "Growth")
df_s <- completeFun(df_s, "Pro")
df_s <- completeFun(df_s, "Zoox")
df_s_l <- gather(df_s, param, value, 4:6,8)

## specific treatments dataframes
C_df <- subset(df_s, treatment == "Tc") # c
S_df <- subset(df_s, treatment == "T1") # s
F_df <- subset(df_s, treatment == "T2") # p
I_df <- subset(df_s, treatment == "T3") # a

## specific genotypes dataframes
K2_df <- subset(df_s, genotype == "K2") # s
M5_df <- subset(df_s, genotype == "M5") # s
M6_df <- subset(df_s, genotype == "M6") # p

```

## Principal component analyses Ecophys parameters only {.tabset}

#### *Methods:*
Principal component analysis (PCA) (function *prcomp*) of scaled and centered physiological parameters (host protein, algal symbiont chlorophyll a, algal symbiont cell density, percent growth were employed to assess the relationship between physiological parameters treatment conditions amd genotype for each coral. Main effects (treatment (Sprinkler- feeding & interactive), genotype) were evaluated with PERMANOVA using the *adonis2* function (*vegan* package; version `r packageVersion("vegan")` (Oksanen et al., 2020)).


<br/>

### interactive treatment and genotype
```{r}
# set up the dataframe
cat_pca_df <- df_s[,c(4:6,8)]

# run the adonis
cat_pca_mod <- adonis2(cat_pca_df ~ treatment*genotype, data = df_s, method = 'eu', permutations = bootnum)
cat_pca_mod # view  adonis output
# extract pvalues
cat_pval <- cat_pca_mod["Pr(>F)"]
# perform principal component analysis (PCA)
cat_pca <- prcomp(cat_pca_df, center = TRUE, scale= TRUE)
cat_pca
```

```{r}
catEig<- get_eig(cat_pca)
catEig
var <- get_pca_var(cat_pca)
names(var)
head(var$coord)
head(var$cor)
head(var$contrib)
#zoox 43%- Pro 40% PC1
#growth 78%- Pro 13% PC2
corrplot(var$contrib, is.corr=FALSE)
fviz_eig(cat_pca, addlabels =TRUE)
fviz_pca_var(cat_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07")
             )
```

```{r interaction (treatment*genotype) PCA plot}
# create labels for p values calculated above
g_cat_pval <-substitute(italic(P[genotype])==p, list(p = format(cat_pval[2,1], digits = 1)))
t_cat_pval <-substitute(italic(P[treatment])==p, list(p = format(cat_pval[1,1], digits = 1)))
I_cat_pval <-substitute(italic(P[geno:treat])==p, list(p = format(cat_pval[3,1], digits = 2)))

# genotype across Treatment 1
# Treatment
Interg_cat_pca2 <- autoplot(cat_pca, data = df_s, 
         colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.level= 0.95,
         frame.alpha = 0.0,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE, 
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = 5, 
         loadings.label.vjust = 0.5,
         loadings.label.repel = TRUE) +
          scale_fill_manual(values = c('red','green4', 'blue'))+
    #scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
    #guides(color = guide_legend(keyheight = 0.3, nrow = 6, byrow = TRUE, override.aes = list(linetype = c(0, 0)))) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = 0.0, y = -.75, label = deparse(g_cat_pval), parse = TRUE, size = 3)+
  ggtitle(expression(paste(bold("A)   "), "Genotype")))


Interg_cat_pca2
ggsave("Interg_cat_pca2.pdf")


Intert_cat_pca2 <- autoplot(cat_pca, data = df_s, 
                           colour = "treatment",
                           shape = "genotype",
                           #size=3,
                           alpha=5,
                           fill = "treatment",               
                           frame = TRUE, 
                           frame.type = "norm",
                           frame.level= 0.95,
                           frame.alpha = 0.0,
                           loadings = TRUE, 
                           loadings.colour = "black", 
                           loadings.label = TRUE, 
                           loadings.label.colour = "black",         
                           loadings.label.size = 4, 
                           loadings.label.hjust = 5, 
                           loadings.label.vjust = 0.5,
                           loadings.label.repel = TRUE) +
  scale_color_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
  annotate("text", x = 0.0, y = -.75, label = deparse(t_cat_pval), parse = TRUE, size = 3)+
  ggtitle(expression(paste(bold("   "), "Treatment")))

Intert_cat_pca2
ggsave("Intert_cat_pca2.pdf")

```

### **Figure 1**

```{r}
inter_PCA <- ggarrange( Interg_cat_pca,Intert_cat_pca, ncol = 2, common.legend = FALSE, legend = "right")
inter_PCA
ggarrange(inter_PCA) 
ggsave("inter_PCA2.pdf")

```

### Subset data frame to analyze the difference between genotypes across treatments

```{r}
## specific treatments dataframes
S_df <- subset(df_s, treatment == "T1") # s
F_df <- subset(df_s, treatment == "T2") # p
I_df <- subset(df_s, treatment == "T3") # a
C_df <- subset(df_s, treatment == "Tc") # c
```

### Sprinkler Treatment
```{r}
# set up the dataframe
S_df <- unique(S_df) # remove any duplicate rows
s_df_l <- gather(S_df, param, value, c(4:6,8))
spr_pca_df <- S_df[,c(4:6,8)]

# run the adonis
s_pca_mod <- adonis2(spr_pca_df ~ genotype, data = S_df, method = 'eu', permutations = bootnum)
s_pca_mod # view  adonis output
summary(s_pca_mod)
# extract pvalues
s_pval <- s_pca_mod["Pr(>F)"]
# perform principal component analysis (PCA)
s_pca <- prcomp(spr_pca_df, center = TRUE, scale= TRUE)
s_pca
```

```{r}
SEig<- get_eig(s_pca)
SEig
var <- get_pca_var(s_pca)
names(var)
head(var$coord)
head(var$cor)
head(var$contrib)
#zoox 38%- Pro 27% PC1
#growth 68%- Pro 28% PC2
corrplot(var$contrib, is.corr=FALSE)
fviz_pca_var(s_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07")
             )
```


```{r sprinkler (T1) PCA plot}

# create labels for p values calculated above
s_geno_pval <-substitute(italic(P[genotype])==p, list(p = format(s_pval[1,1], digits = 1)))
# genotype across Treatment 1
# Treatment sprinkler

T1_geno_pca <- autoplot(s_pca, data = S_df, 
          colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.level= 0.95,
         frame.alpha = 0,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 5, 
         loadings.label.hjust = 2.5, 
         loadings.label.vjust = 1,
         loadings.label.repel = TRUE) +
        scale_fill_manual(values = c('red','green4', 'blue'))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE)) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = 0.0, y = -1.8, label = deparse(s_geno_pval), parse = TRUE, size = 3)+  ggtitle(expression(paste(bold("A)   "), "Sprinkler")))

T1_geno_pca
ggsave("T1_geno_pca2.pdf")

```

### Feeding Treatment

```{r}
# set up the dataframe
F_df <- unique(F_df) # remove any duplicate rows
f_df_l <- gather(F_df, param, value, c(4:6,8))
feed_pca_df <- F_df[,c(4:6,8)]

# run the adonis
f_pca_mod <- adonis2(feed_pca_df ~ genotype, data = F_df, method = 'eu', permutations = bootnum)
f_pca_mod # view  adonis output
# extract pvalues
f_pval <- f_pca_mod["Pr(>F)"]
# perform principal component analysis (PCA)
f_pca <- prcomp(feed_pca_df, center = TRUE, scale= TRUE)
f_pca
```


```{r}
FEig<- get_eig(f_pca)
FEig
var <- get_pca_var(f_pca)
names(var)
head(var$coord)
head(var$cor)
head(var$contrib)
#Pro 44% growth 33% PC1
#Chlo 63%- growth  27% PC2
corrplot(var$contrib, is.corr=FALSE)
fviz_pca_var(f_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07")
             )
```


```{r Feeding (T2) PCA plot}

# create labels for p values calculated above
f_geno_pval <-substitute(italic(P[genotype])==p, list(p = format(f_pval[1,1], digits = 1)))
# genotype across Treatment 2
# Treatment Feeding
T2_geno_pca <- autoplot(f_pca, data = F_df, 
          colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.level= 0.95,
         frame.alpha = 0,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 5, 
         loadings.label.hjust = 2.5, 
         loadings.label.vjust = 1,
         loadings.label.repel = TRUE) +
        scale_fill_manual(values = c('red','green4', 'blue'))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE)) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = 0.0, y = -1.8, label = deparse(f_geno_pval), parse = TRUE, size = 3)+  ggtitle(expression(paste(bold("B)   "), "Feeding")))



T2_geno_pca
ggsave("T2_geno_pca2.pdf")

```

### Interactive Sprinkler:Feeding Treatment
```{r}
I_df 
# set up the dataframe
I_df <- unique(I_df) # remove any duplicate rows
i_df_l <- gather(I_df, param, value, c(4:6,8))
inte_pca_df <- I_df[,c(4:6,8)]

# run the adonis
i_pca_mod <- adonis2(inte_pca_df ~ genotype, data = I_df, method = 'eu', permutations = bootnum)
i_pca_mod # view  adonis output
# extract pvalues
i_pval <- i_pca_mod["Pr(>F)"]
# perform principal component analysis (PCA)
i_pca <- prcomp(inte_pca_df, center = TRUE, scale= TRUE)
i_pca
```

```{r}
IEig<- get_eig(i_pca)
IEig
var <- get_pca_var(i_pca)
names(var)
head(var$coord)
head(var$cor)
head(var$contrib)
#Chlor 39% Zoox 32% PC1
#growth  65%  Pro 24% PC2
corrplot(var$contrib, is.corr=FALSE)
fviz_pca_var(i_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07")
             )
```

```{r Interactive (T3) PCA plot}

# create labels for p values calculated above
i_geno_pval <-substitute(italic(P[genotype])==p, list(p = format(i_pval[1,1], digits = 1)))
# genotype across Treatment 2
# Treatment Feeding
T3_geno_pca <- autoplot(i_pca, data = I_df, 
         colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.level= 0.95,
         frame.alpha = 0,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 5, 
         loadings.label.hjust = 2.5, 
         loadings.label.vjust = 1,
         loadings.label.repel = TRUE) +
        scale_fill_manual(values = c('red','green4', 'blue'))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE)) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = 0.0, y = -1.8, label = deparse(i_geno_pval), parse = TRUE, size = 3)+  ggtitle(expression(paste(bold("C)   "), "Interactive")))


T3_geno_pca
ggsave("T3_geno_pca2.pdf")

```

### Control Treatment
```{r}
C_df 
# set up the dataframe
C_df <- unique(C_df) # remove any duplicate rows
c_df_l <- gather(C_df, param, value, c(4:6,8))
cont_pca_df <- C_df[,c(4:6,8)]

# run the adonis
c_pca_mod <- adonis2(cont_pca_df ~ genotype, data = C_df, method = 'eu', permutations = bootnum)
c_pca_mod # view  adonis output
# extract pvalues
c_pval <- i_pca_mod["Pr(>F)"]
# perform principal component analysis (PCA)
c_pca <- prcomp(cont_pca_df, center = TRUE, scale= TRUE)
c_pca
summary(c_pca)
```

```{r}
CEig<- get_eig(c_pca)
CEig
var <- get_pca_var(c_pca)
names(var)
head(var$coord)
head(var$cor)
head(var$contrib)
# zoox 37% Chlo/Pro 30% PC1
# Growth 62% PC2
corrplot(var$contrib, is.corr=FALSE)
fviz_pca_var(c_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07")
             )
```


```{r Control (Tc) PCA plot}

# create labels for p values calculated above
c_geno_pval <-substitute(italic(P[genotype])==p, list(p = format(c_pval[1,1], digits = 1)))
# genotype across Treatment 2
# Treatment Feeding
Tc_geno_pca <- autoplot(c_pca, data = C_df, 
          colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.level= 0.95,
         frame.alpha = 0,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 5, 
         loadings.label.hjust = 2.5, 
         loadings.label.vjust = 1,
         loadings.label.repel = TRUE) +
        scale_fill_manual(values = c('red','green4', 'blue'))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE)) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = 0.0, y = -1.8, label = deparse(c_geno_pval), parse = TRUE, size = 3)+  ggtitle(expression(paste(bold("D)   "), "Control")))



Tc_geno_pca
ggsave("Tc_geno_pca2.pdf")

```

### Subset data frame to analyze the difference across treatments in each genotype

```{r}
## specific genotypes dataframes
K2_df <- subset(df_s, genotype == "K2") # s
M5_df <- subset(df_s, genotype == "M5") # s
M6_df <- subset(df_s, genotype == "M6") # p
```

### K2 genotype

```{r}
K2_df 
# set up the dataframe
K2_df <- unique(K2_df) # remove any duplicate rows
K2_df_l <- gather(K2_df, param, value, c(4:6,8))
K2_pca_df <- K2_df[,c(4:6,8)]

# run the adonis
K2_pca_mod <- adonis2(K2_pca_df ~ treatment, data = K2_df, method = 'eu', permutations = bootnum)
K2_pca_mod # view  adonis output
# extract pvalues
K2_pval <- K2_pca_mod["Pr(>F)"]
# perform principal component analysis (PCA)
K2_pca <- prcomp(K2_pca_df, center = TRUE, scale= TRUE)
```

```{r}
catEig<- get_eig(K2_pca)
catEig
var <- get_pca_var(K2_pca)
names(var)
head(var$coord)
head(var$cor)
head(var$contrib)
#
#
corrplot(var$contrib, is.corr=FALSE)
fviz_eig(K2_pca, addlabels =TRUE)
fviz_pca_var(K2_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07")
             )
```

```{r K2 (treatments) PCA plot}

# create labels for p values calculated above
K2_treat_pval <-substitute(italic(P[treatment])==p, list(p = format(K2_pval[1,1], digits = 1)))
#K2 genotype and all treatments
K2_geno_pca <- autoplot(K2_pca, data = K2_df,
                        colour = "treatment",
                           shape = "treatment",
                           #size=3,
                           alpha=5,
                           fill = "treatment",               
                           frame = TRUE, 
                           frame.type = "norm",
                           frame.level= 0.95,
                           frame.alpha = 0.0,
                           loadings = TRUE, 
                           loadings.colour = "black", 
                           loadings.label = TRUE, 
                           loadings.label.colour = "black",         
                           loadings.label.size = 4, 
                           loadings.label.hjust = 5, 
                           loadings.label.vjust = 0.5,
                           loadings.label.repel = TRUE) +
  scale_color_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
  annotate("text", x = 0.0, y = -1.75, label = deparse(K2_treat_pval), parse = TRUE, size = 3)+
  ggtitle(expression(paste(bold("A)   "), "K2")))
         


K2_geno_pca
ggsave("K2_geno_pca2.pdf")

```

### M5 genotype

```{r}
M5_df 
# set up the dataframe
M5_df <- unique(M5_df) # remove any duplicate rows
M5_df_l <- gather(M5_df, param, value, c(4:6,8))
M5_pca_df <- M5_df[,c(4:6,8)]

# run the adonis
M5_pca_mod <- adonis2(M5_pca_df ~ treatment, data = M5_df, method = 'eu', permutations = bootnum)
M5_pca_mod # view  adonis output
# extract pvalues
M5_pval <- M5_pca_mod["Pr(>F)"]
# perform principal component analysis (PCA)
M5_pca <- prcomp(M5_pca_df, center = TRUE, scale= TRUE)
```


```{r M5 (treatments) PCA plot}

# create labels for p values calculated above
M5_treat_pval <-substitute(italic(P[treatment])==p, list(p = format(M5_pval[1,1], digits = 1)))
#M5 genotype and all treatments
M5_geno_pca <- autoplot(M5_pca, data = M5_df, 
         colour = "treatment",
                           shape = "treatment",
                           #size=3,
                           alpha=5,
                           fill = "treatment",               
                           frame = TRUE, 
                           frame.type = "norm",
                           frame.level= 0.95,
                           frame.alpha = 0.0,
                           loadings = TRUE, 
                           loadings.colour = "black", 
                           loadings.label = TRUE, 
                           loadings.label.colour = "black",         
                           loadings.label.size = 4, 
                           loadings.label.hjust = 5, 
                           loadings.label.vjust = 0.5,
                           loadings.label.repel = TRUE) +
  scale_color_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
  annotate("text", x = 0.0, y = -1.75, label = deparse(M5_treat_pval), parse = TRUE, size = 3)+
  ggtitle(expression(paste(bold("B)   "), "M5")))



M5_geno_pca
ggsave("M5_geno_pca2.pdf")

```

```{r}
catEig<- get_eig(M5_pca)
catEig
var <- get_pca_var(M5_pca)
names(var)
head(var$coord)
head(var$cor)
head(var$contrib)
#
#
corrplot(var$contrib, is.corr=FALSE)
fviz_eig(M5_pca, addlabels =TRUE)
fviz_pca_var(M5_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07")
             )
```

### M6 genotype

```{r}
M6_df 
# set up the dataframe
M6_df <- unique(M6_df) # remove any duplicate rows
M6_df_l <- gather(M6_df, param, value, c(4:6,8))
M6_pca_df <- M6_df[,c(4:6,8)]

# run the adonis
M6_pca_mod <- adonis2(M6_pca_df ~ treatment, data = M6_df, method = 'eu', permutations = bootnum)
M6_pca_mod # view  adonis output
# extract pvalues
M6_pval <- M6_pca_mod["Pr(>F)"]
# perform principal component analysis (PCA)
M6_pca <- prcomp(M6_pca_df, center = TRUE, scale= TRUE)
```

```{r M6 (treatments) PCA plot}

# create labels for p values calculated above
M6_treat_pval <-substitute(italic(P[treatment])==p, list(p = format(M6_pval[1,1], digits = 1)))
#M6 genotype and all treatments
M6_geno_pca <- autoplot(M6_pca, data = M6_df, 
         colour = "treatment",
                           shape = "treatment",
                           #size=3,
                           alpha=5,
                           fill = "treatment",               
                           frame = TRUE, 
                           frame.type = "norm",
                           frame.level= 0.95,
                           frame.alpha = 0.0,
                           loadings = TRUE, 
                           loadings.colour = "black", 
                           loadings.label = TRUE, 
                           loadings.label.colour = "black",         
                           loadings.label.size = 4, 
                           loadings.label.hjust = 5, 
                           loadings.label.vjust = 0.5,
                           loadings.label.repel = TRUE) +
  scale_color_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
  annotate("text", x = 0.0, y = -1.75, label = deparse(M6_treat_pval), parse = TRUE, size = 3)+
  ggtitle(expression(paste(bold("C)   "), "M6")))

M6_geno_pca
ggsave("M6_geno_pca2.pdf")

```

```{r}
catEig<- get_eig(M6_pca)
catEig
var <- get_pca_var(M6_pca)
names(var)
head(var$coord)
head(var$cor)
head(var$contrib)
#
#
corrplot(var$contrib, is.corr=FALSE)
fviz_eig(M6_pca, addlabels =TRUE)
fviz_pca_var(M6_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07")
             )
```


### **Figure 2 & 3**

```{r PCA plot}
#Figure 2
geno_PCA <- ggarrange(T1_geno_pca,T2_geno_pca,T3_geno_pca,Tc_geno_pca, ncol = 4, common.legend = TRUE, legend = "right")
ggarrange(geno_PCA) 
ggsave("geno_PCA.pdf")
#Figure 3
treat_PCA <- ggarrange(K2_geno_pca, M5_geno_pca, M6_geno_pca, ncol = 3, common.legend = TRUE, legend = "right")
ggarrange(treat_PCA) 
ggsave("treat_PCA.pdf")
```


##########################################################################################

<br/>

## Correlation assessments {.tabset}

#### *Methods:*
Correlations (Correlation test is used to evaluate the association between two or more variables.) among all physiological parameters were assessed to determine the relationships between parameters within each genotype and treatment The Pearson correlation coefficient (R^2^) of each comparison was calculated using the rcorr package (version `r packageVersion("rcorr")` and the significance was calculated using the *cor.test* function. These relationships were then visualized through simple scatterplots.

<br/>


```{r}
S_df 
F_df 
I_df 
C_df 
K2_df
M5_df
M6_df

```


Correlation matrix The function rcorr() [in Hmisc package] can be used to compute the significance levels for pearson and spearman correlations. It returns both the correlation coefficients and the p-value of the correlation for all possible pairs of columns in the data table.
```{r}
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}
## create matrix for correlations for all
S_corr_df2 <- rcorr(as.matrix(S_df[, c(4:6,8)])) #
S_corr_df2 # correlation matrix
S_corr_df2$r  # R2 of all correlations
S_corr_df2$P  # P value of all correlations
S_corr_df2$r[S_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)
flattenCorrMatrix(S_corr_df2$r, S_corr_df2$P)
#Pro- Zoox 0.28
#Growth- Zoox 0.217 
#NS


pdf(file = "S_corr_df2.pdf")

corrplot(S_corr_df2$r, type="upper", order="hclust", 
         p.mat = S_corr_df2$P, sig.level = 0.05, insig = "blank")

grid.echo()

S_corr_df <- grid.grab()

dev.off()

F_corr_df2 <- rcorr(as.matrix(F_df[, c(4:6,8)])) #
F_corr_df2 # correlation matrix
F_corr_df2$r  # R2 of all correlations
F_corr_df2$P  # P value of all correlations
F_corr_df2$r[F_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)
flattenCorrMatrix(F_corr_df2$r, F_corr_df2$P)


pdf(file = "F_corr_df2.pdf")

corrplot(F_corr_df2$r, type="upper", order="hclust", 
         p.mat = F_corr_df2$p, sig.level = 0.05, insig = "blank")
grid.echo()

F_corr_df <- grid.grab()

dev.off()

I_corr_df2 <- rcorr(as.matrix(I_df[, c(4:6,8)])) #
I_corr_df2 # correlation matrix
I_corr_df2$r  # R2 of all correlations
I_corr_df2$P  # P value of all correlations
I_corr_df2$r[I_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)
flattenCorrMatrix(I_corr_df2$r, I_corr_df2$P)

pdf(file = "I_corr_df2.pdf")

corrplot(I_corr_df2$r, type="upper", order="hclust", 
         p.mat = I_corr_df2$p, sig.level = 0.05, insig = "blank")

grid.echo()

I_corr_df <- grid.grab()

dev.off()

## create matrix for correlations by treatment
C_corr_df2 <- rcorr(as.matrix(C_df[, c(4:6,8)])) #
C_corr_df2 # correlation matrix
C_corr_df2$r  # R2 of all correlations
C_corr_df2$P  # P value of all correlations
C_corr_df2$r[C_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)
flattenCorrMatrix(C_corr_df2$r, C_corr_df2$P)
#Chlo   Zoox  0.60266151 0.0380749338
#Chlo Growth  0.62102806 0.0311463441
#Pro   Zoox  0.85782868 0.0003585313


pdf(file = "C_corr_df2.pdf")

corrplot(C_corr_df2$r, type="upper", order="hclust", 
         p.mat = C_corr_df2$p, sig.level = 0.05, insig = "blank")

grid.echo()

C_corr_df <- grid.grab()

dev.off()

## create matrix for correlations by genotype
K2_corr_df2 <- rcorr(as.matrix(K2_df[, c(4:6,8)])) #
K2_corr_df2 # correlation matrix
K2_corr_df2$r  # R2 of all correlations
K2_corr_df2$P  # P value of all correlations
K2_corr_df2$r[K2_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)
flattenCorrMatrix(K2_corr_df2$r, K2_corr_df2$P)

pdf(file = "K2_corr_df2.pdf")

corrplot(K2_corr_df2$r, type="upper", order="hclust", 
         p.mat = K2_corr_df2$p, sig.level = 0.05, insig = "blank")


grid.echo()

K2_corr_df <- grid.grab()

dev.off()

M5_corr_df2 <- rcorr(as.matrix(M5_df[, c(4:6,8)])) #
M5_corr_df2 # correlation matrix
M5_corr_df2$r  # R2 of all correlations
M5_corr_df2$P  # P value of all correlations
M5_corr_df2$r[M5_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)
flattenCorrMatrix(M5_corr_df2$r, M5_corr_df2$P)
                  #Cor        Pvalue
#1    Pro   Chlo  0.33218640 0.2087419
#2    Pro Growth -0.04560787 0.8668043
#3   Chlo Growth -0.07300049 0.7881811
#4    Pro   Zoox  0.86518972 1.508012e-05 1.51e-05
#5   Chlo   Zoox  0.41968841 0.1055904
#6 Growth   Zoox -0.06872059 0.8003589

pdf(file = "M5_corr_df2.pdf")

corrplot(M5_corr_df2$r, type="upper", order="hclust", 
         p.mat = M5_corr_df2$p, sig.level = 0.05, insig = "blank")
grid.echo()

M5_corr_df <- grid.grab()

dev.off()

M6_corr_df2 <- rcorr(as.matrix(M6_df[, c(4:6,8)])) #
M6_corr_df2 # correlation matrix
M6_corr_df2$r  # R2 of all correlations
M6_corr_df2$P  # P value of all correlations
M6_corr_df2$r[M6_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)
flattenCorrMatrix(M6_corr_df2$r, M6_corr_df2$P)


pdf(file = "M6_corr_df2.pdf")

corrplot(M6_corr_df2$r, type="upper", order="hclust", 
         p.mat = M6_corr_df2$p, sig.level = 0.05, insig = "blank")

grid.echo()

M6_corr_df <- grid.grab()

dev.off()
```



