---
title: "Acropora_DataCleaning_Ecophys"
author: "Gould, Katelyn"
date: "10/2/2019"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: kable 
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

#Description
In this file I combine all the ecophysiological data (zooxanthella densities, chlorophyll a concentration, surface area, growth rate, and protein content extracted from Acropora cervicornis corals that were flash frozen in liquid nitrogen on April 24th 2017. Corals were then processed in the lab at the University of North Carolina at Chapel Hill in June-August 2019. 
</br></br>
## What is in this file?
Data cleaning for further analyses using `tidyverse` (and a few other) packages
</br></br>


```{r setup, results='hide', message=FALSE}
knitr::opts_chunk$set(echo = TRUE) # will automatically include code in the ouput unless we state otherwise
knitr::opts_chunk$set(warning= FALSE) # will NOT include warning messages in the output unless we state otherwise
# knitr::opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE) #keeps code wrapped in the output

# if you haven't installed these packages run the following line (first delete the # sign):
#install.packages(c("tidyverse", "janitor", "kableExtra", "cowplot", "skimr", "measurements"))

library(tidyverse) #data wrangling & cleaning incl. ggplot
library(janitor) # more data cleaning functions
library(kableExtra) # making pretty tables
library(cowplot) # making publication quality figures or multi-panel figures
library(skimr) # tool to get quick overview of dataset
library(measurements) # useful to convert units
library(readr)
library(esquisse)
library(rvg)
library(car)
library(ggpubr)
library(plotrix)
library(mvnormtest)

```
</br></br>

# Data
For this common garden experiment, we will upload ecophys data extrapolated from frozen Acropora cervicornis corals in June-August 2019. 
This experiment is esimating the differences between three treatments and a control aquarium for the various ecophys factors:
* Metabolic rates "Fitness" (Gross Photosynthesis, Respiration) umol/cm2/hr _See: Data_Manipultion_final.csv, and TPCs_ALL_acropora_final.csv_
* Growth rates are in _% larger than the intial value.
* Protein Concentration ug/cm2 (coral tissue)
* Zooxanthella densities Zoox/coral, cm2, log(Zoox/cm2), & Zoox/protein
* Chlorophylla a concentration Chl/zoox (pg), Chl/protein, ug/cm2, log(ug/cm2)
</br></br>
Some important notes:  
* Surface area in cm^2 was estimated via 3D scans
* Growth rates were estimated via buoyant weights taken before and after the experimental temperature ramping and is in %
* Protein, chlorophyll a, and zooxanthella density are all standardized to Surface area. 
* Coral ID's represent the Genotypes: K2, M5 & M6 followed by treatment 01 (Sprinkler), 02 (Lights), 03 (lights & sprinkler), & C (control).


</br></br>

__Read in bleaching Data__
```{r data_import}

setwd("C:/Github/TPC_Acropora/Raw_data")
getwd()

data<-read.csv("C:/Github/TPC_Acropora/Raw_data/Ecophys_data/TidyEcopphysData.csv")

```
</br></br>

```{r data_review}
# review variables and class types
str(data)

# use the janitor package to clean up column names- lowercase, no spaces
data <- janitor::clean_names(data)

# We can do some manual investigation of the data:
  # How many unqiue coral reefs are included in this dataset?
length(unique(data$genotype)) #4
length(unique(data$coral_id)) #52
# What are the different substrate codes?
unique(data$treatment) # 1,2,3,c,i

T0data<-data%>%
  filter(treatment=="i")%>%
  filter(genotype!="M7")

T0data$totzoox<-T0data$zoox_cm2_3d/100000

T0data$logzoo<-log(T0data$zoox_cm2_3d+1)
T0data$logprotein<-log(T0data$protein_3d_ug_cm2+1)
T0data$logchl_ug_cm2<-log(T0data$chl_ug_cm2+1)

Dtest<-data%>%
  filter(treatment!="i")
Dtest%>% filter(genotype!="M7")
data<-Dtest
# Use the kableExtra package to view a pretty table for a subset of the data:
  # First, let's just subset the first 10 rows
RawDataTab<-data%>% 
    # Add a title
  kableExtra::kable(caption="Raw Ecophys") %>% 
    # Specify how we will see the table, type ?kablestyling to see explanations and options
  kable_styling(bootstrap_options = "condensed", full_width=F) 

```

```{r skimr, results='hide'}

# And we can use the skimr package to review the dataset
skimr::skim(data)


data$treatment <- sub("^", "T", data$treatment )
data$treatment<-factor(data$treatment)
#write.csv(data,"C:/Github/TPC_Acropora/data.csv")
```


xtabs(~ genotype + treatment, data = data)
 treatment
genotype 1 2 3 c i
      K2 4 4 4 4 2
      M5 4 4 4 4 1
      M6 4 4 4 4 1
      M7 0 0 0 0 1

# PROTEIN/CM2
Total Protein

```{r}
plab<-expression(paste("Total protein ( "*mu,"g cm"^-2,")"))

ggplot(data, aes(y=protein_3d_ug_cm2, x=treatment, fill = genotype)) + 
  geom_boxplot() + 
  ylab(plab)+
  theme_classic()
```

## Look at all dependent variables and check for skewedness

```{r}

##Checking non logged transformed portein data
ggdensity(data$protein_3d_ug_cm2, 
          main = "Density plot of protein",
          xlab = "Protein content")
#SKEWED
ggqqplot(data$protein_3d_ug_cm2)
shapiro.test(data$protein_3d_ug_cm2)
#2.053e-6

data$logprotein<-log(data$protein_3d_ug_cm2+1)

ggdensity(data$logprotein, 
          main = "Density plot of protein",
          xlab = "Protein content")
#SKEWED
ggqqplot(data$logprotein)
shapiro.test(data$logprotein)
#0.0007 
# The data did not pass th shapiro test- I will transform the data with logit to see if that can solve the problem of normality
#logit transform 0-100
data$logitprotein<-car::logit(data$protein_3d_ug_cm2)


ggdensity(data$logitprotein, 
          main = "Density plot of protein",
          xlab = "Protein content")
#SKEWED
ggqqplot(data$logitprotein)
shapiro.test(data$logitprotein)
#0.03211

shapiro.test(data$protein_3d_ug_cm2)

bartlett.test(protein_3d_ug_cm2~interaction(treatment,genotype), data=data)
bartlett.test(protein_3d_ug_cm2~treatment, data=data)
bartlett.test(protein_3d_ug_cm2~genotype, data=data)
#did not pass bartlett
leveneTest(protein_3d_ug_cm2~treatment, data=data)
leveneTest(protein_3d_ug_cm2~genotype, data=data)
leveneTest(protein_3d_ug_cm2 ~ treatment*genotype, data = data)
fligner.test(protein_3d_ug_cm2~treatment, data=data)
fligner.test(protein_3d_ug_cm2~genotype, data=data)
# It still is not normal, nor is the variance equal therefore I will use a non-parametric test on the non-transformed raw data to assess the protein content/cm2 of the corals to find differences 

# Due to the small sample size of n=48, the non-normality of both logged and logit transformed data not passing the shapiro test I will priceed with a nonparametric test (distribution free test) for this dependent variable
#The modules on hypothesis testing presented techniques for testing the equality of means in two independent samples. An underlying assumption for appropriate use of the tests described was that the continuous outcome was approximately normally distributed or that the samples were sufficiently large (usually n1> 30 and n2> 30) to justify their use based on the Central Limit Theorem
# Nonparametric test options: 
# 1) Mann Whitney U Test AKA Wilcoxon Rank Sum test [akin to comparing the medians between the two populations "matched or paired data only"]=For any Mann-Whitney U test, the theoretical range of U is from 0 (complete separation between groups, H0 most likely false and H1 most likely true) to n1*n2 (little evidence in support of H1)
#2) **Kruskal Wallis test [The Kruskal Wallis test is used to compare medians among k comparison groups (k > 2) and is sometimes described as an ANOVA with the data replaced by their ranks]  in a Kruskal Wallis test with 3 or more comparison groups and 5 or more observations in each group, the critical value for the test can be found in the table of Critical Values of the χ 2 Distribution**
#
```

Non parametric Kruskal Wallis protein/cm2

```{r}
library(rstatix)
data %>% 
  group_by(genotype,treatment) %>%
  get_summary_stats(protein_3d_ug_cm2, type = "common")

#box plot
ggboxplot(data, x = "treatment", y = "protein_3d_ug_cm2")
ggboxplot(data, x = "genotype", y = "protein_3d_ug_cm2")

#Question: We want to know if there is a significant difference between the average protein content/cm2 of corals in the 4 experimental conditions and among genotypes.

res.kruskal <- data %>% kruskal_test(protein_3d_ug_cm2 ~ treatment)
res.kruskal
# pvalue= 0.0743
res.kruskal2 <- data %>% kruskal_test(protein_3d_ug_cm2 ~ genotype)
res.kruskal2
#0.488

#EFFECT SIZE
#The eta squared, based on the H-statistic, can be used as the measure of the Kruskal-Wallis test effect size. It is calculated as follow : eta2[H] = (H - k + 1)/(n - k); where H is the value obtained in the Kruskal-Wallis test; k is the number of groups; n is the total number of observations (M. T. Tomczak and Tomczak 2014).

#The eta-squared estimate assumes values from 0 to 1 #and multiplied by 100 indicates the percentage of #variance in the dependent variable explained by the #independent variable.
#
#The interpretation values commonly in published #literature are: 0.01- < 0.06 (small effect), 0.06 - #0.14 (moderate effect) and >= 0.14 (large effect).
data %>% kruskal_effsize(protein_3d_ug_cm2 ~ treatment)
# 0.0892-- moderate
data %>% kruskal_effsize(protein_3d_ug_cm2 ~ genotype)
# -0.0125- small
# Pairwise comparisons
pwc <- data %>% 
  dunn_test(protein_3d_ug_cm2 ~ treatment, p.adjust.method = "BH") 
pwc
#NA no differences between treatments Treat 1 and C 0.0592*
pwcg <- data %>% 
  dunn_test(protein_3d_ug_cm2 ~ genotype, p.adjust.method = "BH") 
pwcg
#NA no differences between genotypes
pwc <- pwc %>% add_xy_position(x = "treatment")
pwcg <- pwcg %>% add_xy_position(x = "genotype")

mod<-lm(protein_3d_ug_cm2~treatment*genotype,data)

effects::allEffects(mod)
summary(mod)
#F 1.019 df 36 p-value- 0.4499
data$cat <- paste(data$treatment,data$genotype)
data$cat<-factor(data$cat)
res.kruskalD <- data %>% kruskal_test(protein_3d_ug_cm2 ~ cat)
res.kruskalD
# stat 13.9 df 11 p-value 0.241
#EFFECT SIZE
data %>% kruskal_effsize(protein_3d_ug_cm2 ~ cat)
#0.0794 -moderate
library(dunn.test)
dunn.test(data$protein_3d_ug_cm2, data$cat, method="bh")
#chi-squared = 13.857, df = 11, p-value = 0.24
pwcD <- data %>% 
  dunn_test(protein_3d_ug_cm2 ~ cat, p.adjust.method = "bonferroni") 
pwcD
pwcD <- pwcD %>% add_xy_position(x = "cat")


#setwd("C:/Github/TPC_Acropora/graphs")

ProplotT<-ggboxplot(data, x = "treatment", y = "protein_3d_ug_cm2", color= "black", fill="treatment", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab(plab)+
  xlab('Treatment')+
   theme(legend.position = "none")+
 scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
  stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))+
   stat_pvalue_manual(pwc, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.kruskal, detailed = TRUE),
    caption = get_pwc_label(pwc)
    )

ProplotT
ggexport(ProplotT, filename = "ProplotT.pdf")


ProplotG<-ggboxplot(data, x = "genotype", y = "protein_3d_ug_cm2", color= "black", fill="genotype", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab(plab)+
  xlab('Genotype')+
  theme(legend.position = "none")+
  scale_fill_manual(values = c('red','green4', 'blue'))+
  stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
   stat_pvalue_manual(pwcg, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.kruskal2, detailed = TRUE),
    caption = get_pwc_label(pwcg)
    )

ProplotG
ggexport(ProplotG, filename = "ProplotG.pdf")


ProplotI<-ggboxplot(data, x = "cat", y = "protein_3d_ug_cm2", color= "black", fill="genotype", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab(plab)+
  xlab('')+
  theme(legend.position = "bottom")+
  scale_fill_manual(values = c('red','green4', 'blue'))+
  stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
   stat_pvalue_manual(pwcD, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.kruskalD, detailed = TRUE),
    caption = get_pwc_label(pwcD)
    )
ProplotI

ggexport(ProplotI, filename = "ProplotI.pdf")
```

```{r}
data_np<-data[c(1:3,5,15, 19:21)]
data.table::setnames(idf_np, old = c('protein_3d_ug_cm2','chl_ug_cm2', 'percent_growth', 'totzoox'), new = c('Pro','Chlo','Growth','Zoox'))
idf_np
```

With inital
```{r}
# get all data from intial
## With inital

idf<-read.csv("C:/Github/TPC_Acropora/Raw_data/Ecophys_data/TidyEcopphysData.csv")
idf <- janitor::clean_names(idf)
# read in full dataframe
# remove unnecessary column
#idf$X1 <- NULL
idf<-idf%>%
  filter(genotype!="M7")
# set columns as factors
idf$cat <- paste(idf$treatment,idf$genotype)

idf$cat <- as.factor(idf$cat)
idf$genotype <- as.factor(idf$genotype)
idf$coral_id <- as.factor(idf$coral_id)
idf$treatment <- sub("^", "T", idf$treatment )
idf$treatment <- as.factor(idf$treatment)
idf$totzoox<-idf$zoox_cm2_3d/100000
idf$logzoo<-log(idf$totzoox+1)
idf$logpercent_growth<-log(idf$percent_growth+1)

idf_sp<-idf[,c(1:3,5,15,20, 22:23)]
idf_np<-idf[,c(1:3,5,15, 19:21)]
data.table::setnames(idf_sp, old = c('protein_3d_ug_cm2','chl_ug_cm2', 'logpercent_growth', 'logzoo'), new = c('Pro','Chlo','Log_Growth','Log_Zoox'))
idf_sp
data.table::setnames(idf_np, old = c('protein_3d_ug_cm2','chl_ug_cm2', 'percent_growth', 'totzoox'), new = c('Pro','Chlo','Growth','Zoox'))
idf_np
```


```{r}

## #kruskal 
res.kruskali <- idf_sp %>% kruskal_test(Pro ~ treatment)
res.kruskali
res.kruskal2i <- idf_sp %>% kruskal_test(Pro ~ genotype)
res.kruskal2i
res.kruskalDi <- idf_sp %>% kruskal_test(Pro ~ cat)
res.kruskalDi
# Pairwise comparisons
pwci <- idf_sp %>% 
  dunn_test(Pro ~ treatment, p.adjust.method = "BH") 
pwci

pwcgi <- idf_sp %>% 
  dunn_test(Pro ~ genotype, p.adjust.method = "BH") 
pwcgi

pwcDi <- idf_sp %>% 
  dunn_test(Pro ~ cat, p.adjust.method = "bonferroni") 
pwcDi

#NA no differences between genotypes
pwci <- pwci %>% add_xy_position(x = "treatment")
pwcgi <- pwcgi %>% add_xy_position(x = "genotype")
pwcDi <- pwcDi %>% add_xy_position(x = "cat")



ProplotTi<-ggboxplot(idf_sp, x = "treatment", y = "Pro", color= "black", fill="treatment", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab(plab)+
  xlab('Treatment')+
   theme(legend.position = "none")+
 scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33','white'))+
  stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  scale_x_discrete(breaks=c("Ti","T1", "T2", "T3", "Tc"),
        labels=c("Inital","Sprinkler", "Feeding", "Interactive","Control"))+
   stat_pvalue_manual(pwci, hide.ns = TRUE) +
    labs(
    subtitle = get_test_label(res.kruskali, detailed = TRUE),
    caption = get_pwc_label(pwci)
    )

ProplotTi
ggexport(ProplotTi, filename = "ProplotTi.pdf")


ProplotGi<-ggboxplot(idf_sp, x = "genotype", y = "Pro", color= "black", fill="genotype", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab(plab)+
  xlab('Genotype')+
  theme(legend.position = "none")+
  scale_fill_manual(values = c('red','green4', 'blue', 'white'))+
  stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
   stat_pvalue_manual(pwcgi, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.kruskal2i, detailed = TRUE),
    caption = get_pwc_label(pwcgi)
    )

ProplotGi
ggexport(ProplotGi, filename = "ProplotGi.pdf")


ProplotIi<-ggboxplot(idf_sp, x = "cat", y = "Pro", color= "black", fill="genotype", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab(plab)+
  xlab('')+
  theme(legend.position = "bottom")+
  scale_fill_manual(values = c('red','green4', 'blue','white'))+
  stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
   stat_pvalue_manual(pwcDi, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.kruskalDi, detailed = TRUE),
    caption = get_pwc_label(pwcDi)
    )
ProplotIi

ggexport(ProplotIi, filename = "ProplotIi.pdf")

```

 Density Zoox/cm2

```{r}

data$totzoox<-data$zoox_cm2_3d/100000

# 10^4 
dlab<-expression(paste("Cell density (10"^5,"cells cm"^-2,")"))



ggplot(data, aes(y=totzoox, x=treatment, fill = genotype)) +   geom_boxplot() + 
  ylab(dlab)+
  theme_classic()
```

```{r}

##Checking non logged transformed zoox_cm2_3d data
ggdensity(data$totzoox, 
          main = "Density plot of Zoox/cm2",
          xlab = "Zoox/cm2 coral Tissue")
#SKEWED
ggqqplot(data$totzoox)
shapiro.test(data$totzoox)
#1.04e-06 

#logdata
data$logzoo<-log(data$totzoox+1)
# IS THIS LOGGED CORRECTLY?
# 

ggdensity(data$logzoo, 
          main = "Density plot of Zoox",
          xlab = "Zoox Density")
#SKEWED
ggqqplot(data$logzoo)
shapiro.test(data$logzoo)
#0.1325
bartlett.test(logzoo~interaction(treatment,genotype), data=data)
bartlett.test(logzoo~treatment, data=data)
bartlett.test(logzoo~genotype, data=data)
leveneTest(logzoo~treatment, data=data)
leveneTest(logzoo~genotype, data=data)
leveneTest(logzoo ~ treatment*genotype, data = data)
fligner.test(logzoo~treatment, data=data)
fligner.test(logzoo~genotype, data=data)
# #equal variance and normal data whhen logged- 

```

Parametric test ANOVA lm
```{r}

zoosum<-data %>% 
  group_by(genotype,treatment) %>%
  get_summary_stats(logzoo, type = "common")

zoosumT<-kable(zoosum, digits = 4,
      caption = "Summary statistics for Log Zoox densities",
      col.names = c("Treatment", "Genotype", "Parameter", "n", "Min", "Max", "Median", "IQR", "Mean","SD", "SE", "CI"),
      align = 'c') %>%
  kable_styling(bootstrap_options =
                  c("hover", "responsive", "striped"),
                full_width = F, position = "center")

zoosumT

# Proceed with ANOVA/lm post hoc Tukeys HSD for logged zooxanthellae
zoomoda<-aov(logzoo~genotype*treatment,data)
summary(zoomoda)
#treatment diff 0.00295
pairwise.t.test(data$logzoo, data$treatment,
                p.adjust.method = "BH")
#1 & 2 0.008 
#2 & C 0.008


pairwise.t.test(data$logzoo, data$genotype,
                p.adjust.method = "BH")
#NS

pairwise.t.test(data$logzoo,data$cat,
                p.adjust.method = "bonf")
#T1M6:T3M5- 0.044
##T1M6:T2K2- 0.025
#more
TukeyHSD(zoomoda)
#M5:T3-M6:T1 -0.07981858 0.0281097
#M6:T2-M6:T1 -0.05909356 0.0327375
#M5:T2-M6:T1 -0.02224300 0.0427180
#K2:T2-M6:T1 -0.14628549 0.0170329
library(Rmisc)
LzootSSt = summarySE(data, measurevar="logzoo",
                     groupvars=c("treatment"))

LzootSSt
LzoogSSt = summarySE(data, measurevar="logzoo",
                     groupvars=c("genotype"))

LzoogSSt
LzooiSSt = summarySE(data, measurevar="logzoo",
                     groupvars=c("cat"))

LzooiSSt
 
Lzootbar<-ggplot(LzootSSt, aes(x=factor(treatment), y=logzoo, fill=treatment)) + 
    geom_bar(stat="identity", width=0.8) +
    geom_errorbar(aes(ymin=logzoo-se, ymax=logzoo+se),
                  width=.2) +
    xlab("") +
ylab(dlab)+
   theme_classic()+
    scale_x_discrete(breaks=c("T1", "T2", "T3", "TC"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))
 Lzootbar
  
LzooImod<-lm(logzoo~genotype*treatment,data)
summary(LzooImod)
# F-  2.877, DF- 36 p-value  0.008168**
Lzootmod<-aov(logzoo~treatment,data)
summary(Lzootmod)
# treat df 3 F=4.844 P= 0.00534
TukeyHSD(Lzootmod)
#T2-T1 0.0119483
#Tc-T2 0.0136503
Lzoogmod<-aov(logzoo~genotype,data)
summary(Lzoogmod)
TukeyHSD(Lzoogmod)
# NSD

LzooImodP<-ggplot(LzooImod, aes(x=treatment, logzoo, fill= genotype))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('')+
  ylab(dlab)+
  theme(legend.position = "bottom")+
  stat_compare_means(label.y=3.5, method = "anova")+
  scale_fill_manual(values = c('red','green4', 'blue'))+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))
LzooImodP

ggexport(LzooImodP, filename = "LzooANOplotinter.pdf")
#######

LzoogmodP<-ggplot(Lzoogmod, aes(x=genotype, logzoo, fill= genotype))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('Genotype')+
  ylab(dlab)+
  theme(legend.position = "none")+
    stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  stat_compare_means(label.y=3.5, method = "anova")+
  scale_fill_manual(values = c('red','green4', 'blue'))
LzoogmodP

ggexport(LzoogmodP, filename = "LzooANOplotgeno.pdf")

LzootmodP<-ggplot(Lzootmod, aes(x=treatment, logzoo, fill= treatment))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('Treatment')+
  ylab(dlab)+
  theme(legend.position = "none")+
      stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  stat_compare_means(label.y=3.5, method = "anova")+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))

LzootmodP
ggexport(LzootmodP, filename = "LzooANOplotrea.pdf")

stat.testi<-aov(logzoo~treatment,data)%>%
  tukey_hsd()

LzoogmodPTu<-ggboxplot(data, x = "treatment", y = "logzoo", fill= "treatment")+
    ylab(dlab)+
  stat_pvalue_manual(
    stat.testi, label = "p.adj", 
    y.position = c(4,5,6,6.5,7,7.5))

plot<-LzoogmodPTu+
    scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
    theme(legend.position = "none")+
    xlab('Treatment')+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))
plot
ggexport(plot, filename = "LzooANOplottreaTUK.pdf")
```

intial 
```{r}
LzooImodi<-lm(Log_Zoox~genotype*treatment,idf_sp)
summary(LzooImodi)
# F-  2.283 on 14 and 36 DF,  p-value: 0.02323***
Lzootmodi<-aov(Log_Zoox~treatment,idf_sp)
summary(Lzootmodi)
# treat df 3 F=3.777 P=  0.00974
TukeyHSD(Lzootmodi)
#T2-T1 -0.69025843 -1.28452788 -0.09598898 0.0154251**
#T3-T1 -0.38866994 -0.98293939  0.20559951 0.3547495
#Tc-T1 -0.01057887 -0.60484832  0.58369058 0.9999985
#Ti-T1 -0.24962001 -1.18924251  0.69000250 0.9422057
#T3-T2  0.30158849 -0.29268096  0.89585794 0.6051601
#Tc-T2  0.67967956  0.08541011  1.27394901 0.0176736**
#Ti-T2  0.44063843 -0.49898408  1.38026093 0.6734227
#Tc-T3  0.37809107 -0.21617838  0.97236052 0.3825169
#Ti-T3  0.13904993 -0.80057257  1.07867244 0.9932607
#Ti-Tc -0.23904113 -1.17866364  0.70058137 0.9502853

Lzoogmodi<-aov(Log_Zoox~genotype,idf_sp)
summary(Lzoogmodi)
TukeyHSD(Lzoogmodi)
# NSD

LzooImodPi<-ggplot(LzooImodi, aes(x=treatment, Log_Zoox, fill= genotype))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('')+
  ylab(dlab)+
  theme(legend.position = "bottom")+
  stat_compare_means(label.y=3.5, method = "anova")+
  scale_fill_manual(values = c('red','green4', 'blue', "white"))+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc", "Ti"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control", "Inital"))
LzooImodPi

ggexport(LzooImodPi, filename = "LzooANOplotinteri.pdf")
#######

LzoogmodPi<-ggplot(Lzoogmodi, aes(x=genotype, Log_Zoox, fill= genotype))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('Genotype')+
  ylab(dlab)+
  theme(legend.position = "none")+
    stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  stat_compare_means(label.y=3.5, method = "anova")+
  scale_fill_manual(values = c('red','green4', 'blue'))
LzoogmodPi

ggexport(LzoogmodPi, filename = "LzooANOplotgenoi.pdf")

LzootmodPi<-ggplot(Lzootmodi, aes(x=treatment, Log_Zoox, fill= treatment))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('Treatment')+
  ylab(dlab)+
  theme(legend.position = "none")+
      stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  stat_compare_means(label.y=3.5, method = "anova")+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33', 'white'))+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc", "Ti"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control",'Inital'))

LzootmodPi
ggexport(LzootmodPi, filename = "LzooANOplotreai.pdf")

stat.testii<-aov(Log_Zoox~treatment,idf_sp)%>%
  tukey_hsd()

LzoogmodPTui<-ggboxplot(idf_sp, x = "treatment", y = "Log_Zoox", fill= "treatment")+
    ylab(dlab)+
  stat_pvalue_manual(
    stat.testii, label = "p.adj", 
    y.position = c(4,5,6,6.5,7,7.5,8,8.5,9,9.5))

ploti<-LzoogmodPTui+
    scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33','white'))+
    theme(legend.position = "none")+
    xlab('Treatment')+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc","Ti"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control", "Inital"))
ploti
ggexport(ploti, filename = "LzooANOplottreaTUKi.pdf")
```


Growth Rate

```{r}
glab<-expression(paste("Growth Rate (%)"))

ggplot(data, aes(y=percent_growth, x=treatment, fill = genotype)) + 
  geom_boxplot() +
  ylab(glab)+
  theme_classic()
```
 Growth rate*100
```{r}

#Checking non logged transformed chl_ug_cm2 data
ggdensity(data$percent_growth, 
          main = "Density plot of percent_growth",
          xlab = "percent_growth of coral")
#Normal
ggqqplot(data$percent_growth)
shapiro.test(data$percent_growth)
#0.01553 

#logdata
data$logpercent_growth<-log(data$percent_growth+1)

ggdensity(data$logpercent_growth, 
          main = "Density plot of Growth Rate",
          xlab = "Growth Rate")
#SKEWED
ggqqplot(data$logpercent_growth)
shapiro.test(data$logpercent_growth)
#0.2879
bartlett.test(logpercent_growth~interaction(treatment,genotype), data=data)
bartlett.test(logpercent_growth~treatment, data=data)
bartlett.test(logpercent_growth~genotype, data=data)
leveneTest(logpercent_growth~treatment, data=data)
leveneTest(logpercent_growth~genotype, data=data)
leveneTest(logpercent_growth ~ treatment*genotype, data = data)
fligner.test(logpercent_growth~treatment, data=data)
fligner.test(logpercent_growth~genotype, data=data)
#equal variance ANOVA/lm
```

Parametric ANOVA/ lm
```{r}
GRsum<-data %>% 
  group_by(genotype,treatment) %>%
  get_summary_stats(logpercent_growth, type = "common")

GRsumT<-kable(GRsum, digits = 4,
      caption = "Summary statistics for Log Zoox/protein densities",
      col.names = c("Treatment", "Genotype", "Parameter", "n", "Min", "Max", "Median", "IQR", "Mean","SD", "SE", "CI"),
      align = 'c') %>%
  kable_styling(bootstrap_options =
                  c("hover", "responsive", "striped"),
                full_width = F, position = "center")

GRsumT

# Proceed with ANOVA/lm post hoc Tukeys HSD for logged zooxanthellae
Lgrmoda<-aov(logpercent_growth~genotype*treatment,data)
summary(Lgrmoda)

#genotype diff 0.000111
pairwise.t.test(data$logpercent_growth, data$treatment,
                p.adjust.method = "bonf")
#NA


pairwise.t.test(data$logpercent_growth, data$genotype,
                p.adjust.method = "bonf")
#K2:M5- 8.2e-5
#M5:M6-. 00092

pairwise.t.test(data$logpercent_growth,data$cat,
                p.adjust.method = "bonf")

#T1K2:T2M5- 0.019
#T3K2:T2M5- 0.0260
#TCK2: T2M5 0.0040

TukeyHSD(Lgrmoda)
#K2:Tc-M5:T2  0.808892555  0.1868168664  1.430968243 0.0030695
#M6:T3-M5:T2  0.642890311  0.0208146232  1.264965999 0.0375670
#K2:T3-M5:T2  0.696491696  0.0744160080  1.318567384 0.0173949
#M5:T2-K2:T2 -0.631559666 -1.2536353543 -0.009483978 0.0439367
#M5:T2-M6:T1 -0.624415283 -1.2464909710 -0.002339595 0.0484383
#M5:T2-K2:T1 -0.853122812 -1.4751984998 -0.231047124 0.0015028
LgrtSSt = summarySE(data, measurevar="logpercent_growth",
                     groupvars=c("treatment"))

LgrtSSt
LgrgSSt = summarySE(data, measurevar="logpercent_growth",
                     groupvars=c("genotype"))

LgrgSSt
LgriSSt = summarySE(data, measurevar="logpercent_growth",
                     groupvars=c("cat"))

LgriSSt
 
Lgrtbar<-ggplot(LgrtSSt, aes(x=factor(treatment), y=logpercent_growth, fill=treatment)) + 
    geom_bar(stat="identity", width=0.8) +
    geom_errorbar(aes(ymin=logpercent_growth-se, ymax=logpercent_growth+se),
                  width=.2) +
    xlab("Treatment") +
  ylab(expression(paste("log", O[2], mu,"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle('Log Growth Rate')+
   theme_classic()+
    scale_x_discrete(breaks=c("T1", "T2", "T3", "TC"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))
 Lgrtbar
  
LgrImod<-lm(logpercent_growth~genotype*treatment,data)
summary(LgrImod)
# F- 3.162, DF- 36 p-value 0.004392*
Lgrtmod<-aov(logpercent_growth~treatment,data)
summary(Lgrtmod)
TukeyHSD(Lgrtmod)
#NA
Lgrgmod<-aov(logpercent_growth~genotype,data)
summary(Lgrgmod)
#df 2 F 11.32  p= 0.000104
TukeyHSD(Lgrgmod)
#M5-K2 -0.4255853  0.0000804
#M6-M5  0.2854627  0.0084194

LgrImodP<-ggplot(LgrImod, aes(x=treatment, logpercent_growth, fill= genotype))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('')+
  ylab(glab)+
  stat_compare_means(label.y=3, method = "anova")+
  scale_fill_manual(values = c('red','green4', 'blue'))+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))
LgrImodP

ggexport(LgrImodP, filename = "LgrANOplotinter.pdf")


LgrgmodP<-ggplot(Lgrgmod, aes(x=genotype, logpercent_growth, fill= genotype))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('Genotype')+
  ylab(glab)+
  theme(legend.position = "none")+
    stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  stat_compare_means(label.y=3, method = "anova")+
  scale_fill_manual(values = c('red','green4', 'blue'))
LgrgmodP

ggexport(LgrgmodP, filename = "LgrANOplotgeno.pdf")

LgrtmodP<-ggplot(Lgrtmod, aes(x=treatment, logpercent_growth, fill= treatment))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('Treatment')+
ylab(glab)+
  theme(legend.position = "none")+
  stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  stat_compare_means(label.y=3, method = "anova")+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))

LgrtmodP
ggexport(LgrtmodP, filename = "LgrANOplotrea.pdf")

stat.testi<-aov(logpercent_growth~genotype,data)%>%
  tukey_hsd()

LgrgmodPTug<-ggboxplot(data, x = "genotype", y = "logpercent_growth", fill= "genotype")+
  ylab(glab)+
  xlab("Genotype")+
    theme(legend.position = "none")+
  stat_pvalue_manual(
    stat.testi, label = "p.adj", 
    y.position = c(3,3.5,4))

plotgr<-LgrgmodPTug+
    scale_fill_manual(values = c('red','green4', 'blue'))
plotgr

ggexport(plotgr, filename = "LgrANOplotgenoTUK.pdf")
```

Inital

```{r}
LgrImodi<-lm(Log_Growth~genotype*treatment,idf_sp)
summary(LgrImodi)
# genotypeM5       0.0238 *  
# treatmentTi     7.5e-08 ***
# F-statistic: 10.63 on 14 and 36 DF,  p-value: 6.476e-09
Lgrtmodi<-aov(Log_Growth~treatment,idf_sp)
summary(Lgrtmodi)
TukeyHSD(Lgrtmodi)
#NA
Lgrgmodi<-aov(Log_Growth~genotype,idf_sp)
summary(Lgrgmodi)
#df 2 F 11.32  p= 0.0.0457
TukeyHSD(Lgrgmodi)
#M5-K2 -0.4255853  0.0000804
#M6-M5  0.2854627  0.0084194

LgrImodPi<-ggplot(LgrImodi, aes(x=treatment, Log_Growth, fill= genotype))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('')+
  ylab(glab)+
  stat_compare_means(label.y=3, method = "anova")+
  scale_fill_manual(values = c('red','green4', 'blue'))+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))
LgrImodPi

ggexport(LgrImodPi, filename = "LgrANOplotinteri.pdf")


LgrgmodPi<-ggplot(Lgrgmodi, aes(x=genotype, Log_Growth, fill= genotype))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('Genotype')+
  ylab(glab)+
  theme(legend.position = "none")+
    stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  stat_compare_means(label.y=3, method = "anova")+
  scale_fill_manual(values = c('red','green4', 'blue'))
LgrgmodPi

ggexport(LgrgmodPi, filename = "LgrANOplotgeno.pdf")
i
LgrtmodPi<-ggplot(Lgrtmodi, aes(x=treatment, Log_Growth, fill= treatment))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('Treatment')+
ylab(glab)+
  theme(legend.position = "none")+
  stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  stat_compare_means(label.y=3, method = "anova")+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33', 'white'))+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc","Ti"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control", "Inital"))

LgrtmodPi
ggexport(LgrtmodPi, filename = "LgrANOplotreai.pdf")

stat.testi<-aov(Log_Growth~genotype,idf_sp)%>%
  tukey_hsd()

LgrgmodPTugi<-ggboxplot(idf_sp, x = "genotype", y = "Log_Growth", fill= "genotype")+
  ylab(glab)+
  xlab("Genotype")+
    theme(legend.position = "none")+
  stat_pvalue_manual(
    stat.testi, label = "p.adj", 
    y.position = c(3,3.5,4))

plotgri<-LgrgmodPTugi+
    scale_fill_manual(values = c('red','green4', 'blue', 'white'))
plotgri

ggexport(plotgri, filename = "LgrANOplotgenoTUKi.pdf")
```

Chl/cm2
```{r}

clab<-expression(paste("Chlorophyll a ( "*mu,"g cm"^-2,")"))

ggplot(data, aes(y=chl_ug_cm2, x=treatment, fill = genotype)) + 
  geom_boxplot() + 
  ylab(clab)+
  theme_classic()
```

```{r}

#Checking non logged transformed chl_ug_cm2 data
ggdensity(data$chl_ug_cm2, 
          main = "Density plot of chl_ug_cm2",
          xlab = "chl_ug_cm2 (pg) of coral")
#SKEWED
ggqqplot(data$chl_ug_cm2)
shapiro.test(data$chl_ug_cm2)
#7.556e-6 

#logdata
data$logchl_ug_cm2<-log(data$chl_ug_cm2+1)

ggdensity(data$logchl_ug_cm2, 
          main = "Density plot of protein",
          xlab = "Protein content")
#SKEWED
ggqqplot(data$logchl_ug_cm2)
shapiro.test(data$logchl_ug_cm2)
#0.04299

#logit transform 0-100
data$logitchl_ug_cm2<-car::logit(data$chl_ug_cm2)


ggdensity(data$logitchl_ug_cm2, 
          main = "Density plot of Chlo",
          xlab = "Chlor content")
#SKEWED
ggqqplot(data$logitchl_ug_cm2)
shapiro.test(data$logitchl_ug_cm2)
#0.4512
bartlett.test(logitchl_ug_cm2~interaction(treatment,genotype), data=data)
leveneTest(logitchl_ug_cm2~treatment, data=data)
leveneTest(logitchl_ug_cm2~genotype, data=data)
leveneTest(logitchl_ug_cm2 ~ treatment*genotype, data = data)
#0.01661-- only test that doesn't pass homogeneity of variance... Do  non-parametertic tests to compare
fligner.test(logitchl_ug_cm2~treatment, data=data)
fligner.test(logitchl_ug_cm2~genotype, data=data)
#equal variance ANOVA/lm
#did not pass Levenes Test - Nonparameteric testing
```

Non-parametric tests on chl_ug_cm2 raw data
```{r}
data %>% 
  group_by(genotype,treatment) %>%
  get_summary_stats(chl_ug_cm2, type = "common")

#box plot
ggboxplot(data, x = "treatment", y = "chl_ug_cm2")
ggboxplot(data, x = "genotype", y = "chl_ug_cm2")

res.kruskal <- data %>% kruskal_test(chl_ug_cm2 ~ treatment)
res.kruskal

res.kruskal2 <- data %>% kruskal_test(chl_ug_cm2 ~ genotype)
res.kruskal2
#0.0409

#EFFECT SIZE
data %>% kruskal_effsize(chl_ug_cm2 ~ treatment)
# -0.0627-- moderate
data %>% kruskal_effsize(chl_ug_cm2 ~ genotype)
# 0.0977- moderate
# Pairwise comparisons
pwc <- data %>% 
  dunn_test(chl_ug_cm2 ~ treatment, p.adjust.method = "BH") 
pwc
#NA no differences
pwcg <- data %>% 
  dunn_test(chl_ug_cm2 ~ genotype, p.adjust.method = "BH") 
pwcg
#K2:M6- 0.0395
pwc <- pwc %>% add_xy_position(x = "treatment")
pwcg <- pwcg %>% add_xy_position(x = "genotype")

mod<-lm(chl_ug_cm2~treatment*genotype,data)

effects::allEffects(mod)
summary(mod)
#F 1.162 df 36 p-value- 0.3463
res.kruskalD <- data %>% kruskal_test(chl_ug_cm2 ~ cat)
res.kruskalD
# stat 12.1 df 11 p-value 0.356
#EFFECT SIZE
data %>% kruskal_effsize(chl_ug_cm2 ~ cat)
# 0.0308 - small
dunn.test(data$chl_ug_cm2, data$cat, method="BH")
#chi-squared = 12.1071, df = 11, p-value = 0.36
pwcD <- data %>% 
  dunn_test(chl_ug_cm2 ~ cat, p.adjust.method = "BH") 
pwcD
pwcD <- pwcD %>% add_xy_position(x = "cat")


ChlorplotT<-ggboxplot(data, x = "treatment", y = "chl_ug_cm2", color= "black", fill="treatment", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab(clab)+
  xlab('Treatment')+
  theme(legend.position = "none")+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
  stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))+
   stat_pvalue_manual(pwc, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.kruskal, detailed = TRUE),
    caption = get_pwc_label(pwc)
    )

ChlorplotT
ggexport(ChlorplotT, filename = "ChlorplotT.pdf")


ChlorplotG<-ggboxplot(data, x = "genotype", y = "chl_ug_cm2", color= "black", fill="genotype", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab(clab)+
  xlab('Genotype')+
 theme(legend.position = "none")+
  scale_fill_manual(values = c('red','green4', 'blue'))+
  stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
   stat_pvalue_manual(pwcg, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.kruskal2, detailed = TRUE),
    caption = get_pwc_label(pwcg)
    )

ChlorplotG
ggexport(ChlorplotG, filename = "ChlorplotG.pdf")


ChlorplotI<-ggboxplot(data, x = "cat", y = "chl_ug_cm2", color= "black", fill="genotype", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab(clab)+
  xlab('')+
 theme(legend.position = "none")+
  scale_fill_manual(values = c('red','green4', 'blue'))+
  stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
   stat_pvalue_manual(pwcD, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.kruskalD, detailed = TRUE),
    caption = get_pwc_label(pwcD)
    )
ChlorplotI

ggexport(ChlorplotI, filename = "ChlorplotI.pdf")


ggboxplot(data, x = "treatment", y = "chl_ug_cm2", color= "black", fill="genotype", outlier.shape = 1) +
  ylab(clab)+
  xlab('Treatment')+
  scale_fill_manual(values = c('red','green4', 'blue'))+
  stat_summary(fun=mean, geom="point", size=2)+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))

ggboxplot(data, x = "genotype", y = "chl_ug_cm2", color= "black", fill="treatment", outlier.shape = 1) +
  ylab(clab)+
  xlab('Genotype')+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))
```



```{r}

## #kruskal 
res.kruskali <- idf_sp %>% kruskal_test(Chlo ~ treatment)
res.kruskali
res.kruskal2i <- idf_sp %>% kruskal_test(Chlo ~ genotype)
res.kruskal2i
res.kruskalDi <- idf_sp %>% kruskal_test(Chlo ~ cat)
res.kruskalDi
# Pairwise comparisons
pwci <- idf_sp %>% 
  dunn_test(Chlo ~ treatment, p.adjust.method = "BH") 
pwci

pwcgi <- idf_sp %>% 
  dunn_test(Chlo ~ genotype, p.adjust.method = "BH") 
pwcgi

pwcDi <- idf_sp %>% 
  dunn_test(Chlo ~ cat, p.adjust.method = "bonferroni") 
pwcDi

#NA no differences between genotypes
pwci <- pwci %>% add_xy_position(x = "treatment")
pwcgi <- pwcgi %>% add_xy_position(x = "genotype")
pwcDi <- pwcDi %>% add_xy_position(x = "cat")

ChlorplotTi<-ggboxplot(idf_sp, x = "treatment", y = "Chlo", color= "black", fill="treatment", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab(clab)+
  xlab('Treatment')+
  theme(legend.position = "none")+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33', "white"))+
  stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc", "Ti"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control", "Inital"))+
   stat_pvalue_manual(pwci, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.kruskali, detailed = TRUE),
    caption = get_pwc_label(pwci)
    )

ChlorplotTi
ggexport(ChlorplotTi, filename = "ChlorplotTi.pdf")


ChlorplotGi<-ggboxplot(idf_sp, x = "genotype", y = "Chlo", color= "black", fill="genotype", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab(clab)+
  xlab('Genotype')+
 theme(legend.position = "none")+
  scale_fill_manual(values = c('red','green4', 'blue', 'white'))+
  stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
   stat_pvalue_manual(pwcgi, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.kruskal2i, detailed = TRUE),
    caption = get_pwc_label(pwcgi)
    )

ChlorplotGi
ggexport(ChlorplotGi, filename = "ChlorplotGi.pdf")


ChlorplotIi<-ggboxplot(idf_sp, x = "cat", y = "Chlo", color= "black", fill="genotype", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab(clab)+
  xlab('')+
 theme(legend.position = "none")+
  scale_fill_manual(values = c('red','green4', 'blue', 'white'))+
  stat_summary(fun=mean, geom="point", size=2)+ #line is median, and closed circle is mean
   stat_pvalue_manual(pwcDi, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.kruskalDi, detailed = TRUE),
    caption = get_pwc_label(pwcDi)
    )
ChlorplotIi

ggexport(ChlorplotIi, filename = "ChlorplotIi.pdf")
```


Zoox:Protein

```{r}
ggplot(data, aes(y=zoox_protein, x=treatment, fill = genotype)) + 
  geom_boxplot() + 
  theme_classic()
```

```{r}

#Checking non logged transformed zoox_protein data
ggdensity(data$zoox_protein, 
          main = "Density plot of Zoox/protein",
          xlab = "Zoox/protein of coral")
#SKEWED
ggqqplot(data$zoox_protein)
shapiro.test(data$zoox_protein)
#2.95e-5 
#logdata
data$logzoopro<-log(data$zoox_protein+1)

ggdensity(data$logzoopro, 
          main = "Density plot of Zoox/protein",
          xlab = "Zoox/protein")
#SKEWED
ggqqplot(data$logzoopro)
shapiro.test(data$logzoopro)
#0.4302
bartlett.test(logzoopro~interaction(treatment,genotype), data=data)
bartlett.test(logzoopro~treatment, data=data)
bartlett.test(logzoopro~genotype, data=data)
leveneTest(logzoopro~treatment, data=data)
leveneTest(logzoopro~genotype, data=data)
leveneTest(logzoopro ~ treatment*genotype, data = data)
fligner.test(logzoopro~treatment, data=data)
fligner.test(logzoopro~genotype, data=data)
# #equal variance and normal data whhen logged- 
```


Parametric test ANOVA lm

```{r}

zooprosum<-data %>% 
  group_by(genotype,treatment) %>%
  get_summary_stats(logzoopro, type = "common")

zooprosumT<-kable(zooprosum, digits = 4,
      caption = "Summary statistics for Log Zoox/protein densities",
      col.names = c("Treatment", "Genotype", "Parameter", "n", "Min", "Max", "Median", "IQR", "Mean","SD", "SE", "CI"),
      align = 'c') %>%
  kable_styling(bootstrap_options =
                  c("hover", "responsive", "striped"),
                full_width = F, position = "center")

zooprosumT

# Proceed with ANOVA/lm post hoc Tukeys HSD for logged zooxanthellae
zoopromoda<-aov(logzoopro~genotype*treatment,data)
summary(zoopromoda)
#treat
#treatment diff 0.00262
pairwise.t.test(data$logzoopro, data$treatment,
                p.adjust.method = "bonf")
#1 & 2 0.011 
#2 & C 0.012


pairwise.t.test(data$logzoopro, data$genotype,
                p.adjust.method = "bonf")
#NS

pairwise.t.test(data$logzoopro,data$cat,
                p.adjust.method = "bonf")

#NS

#more
TukeyHSD(zoopromoda)
#NS
LzooPtSSt = summarySE(data, measurevar="logzoopro",
                     groupvars=c("treatment"))

LzooPtSSt
LzooPgSSt = summarySE(data, measurevar="logzoopro",
                     groupvars=c("genotype"))

LzooPgSSt
LzooPiSSt = summarySE(data, measurevar="logzoopro",
                     groupvars=c("cat"))

LzooPiSSt
 
LzooPtbar<-ggplot(LzooPtSSt, aes(x=factor(treatment), y=logzoopro, fill=treatment)) + 
    geom_bar(stat="identity", width=0.8) +
    geom_errorbar(aes(ymin=logzoopro-se, ymax=logzoopro+se),
                  width=.2) +
    xlab("Treatment") +
  ylab(expression(paste("log", O[2], mu,"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle('Log Zoo/Protein')+
   theme_classic()+
    scale_x_discrete(breaks=c("T1", "T2", "T3", "TC"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))
 LzooPtbar
  
LzooPImod<-lm(logzoopro~genotype*treatment,data)
summary(LzooPImod)
# F- 2.755, DF- 36 p-value 0.01071**
LzooPtmod<-aov(logzoopro~treatment,data)
summary(LzooPtmod)
# treat df 3 F5.122 P= 0.00399
TukeyHSD(LzooPtmod)
#T1:T2- 0.0127561
#T2:Tc- 0.0005931
LzooPgmod<-aov(logzoopro~genotype,data)
summary(LzooPgmod)
TukeyHSD(LzooPgmod)
# NSD

LzooPImodP<-ggplot(LzooPImod, aes(x=treatment, logzoopro, fill= genotype))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('Treatment')+
  ylab(expression(paste(O[2], mu,"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Log Zoox/Protein")+
  stat_compare_means(label.y=15.5, method = "anova")+
  scale_fill_manual(values = c('red','green4', 'blue'))+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))
LzooPImodP

ggexport(LzooPImodP, filename = "LzooPANOplotinter.pdf")


LzooPgmodP<-ggplot(LzooPgmod, aes(x=genotype, logzoopro, fill= genotype))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('Genotype')+
  ylab(expression(paste(O[2], mu,"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Log Zoox/Protein")+
    stat_summary(fun.y=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  stat_compare_means(label.y=15, method = "anova")+
  scale_fill_manual(values = c('red','green4', 'blue'))
LzooPgmodP

ggexport(LzooPgmodP, filename = "LzooPANOplotgeno.pdf")

LzooPtmodP<-ggplot(LzooPtmod, aes(x=treatment, logzoopro, fill= treatment))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('Treatment')+
  ylab(expression(paste(O[2], mu,"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Log Zoox/Protein")+
      stat_summary(fun.y=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  stat_compare_means(label.y=15, method = "anova")+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))

LzooPtmodP
ggexport(LzooPtmodP, filename = "LzooPANOplotrea.pdf")

stat.testi<-aov(logzoopro~treatment,data)%>%
  tukey_hsd()

LzooPgmodPTu<-ggboxplot(data, x = "treatment", y = "logzoopro", fill= "treatment")+
  stat_pvalue_manual(
    stat.testi, label = "p.adj", 
    y.position = c(15,16,16.5,17,17.5,18))

plotzp<-LzooPgmodPTu+
    scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))

ggexport(plotzp, filename = "LzooPANOplottreaTUK.pdf")
```

Chlor/zoox (pg)
```{r}
ggplot(data, aes(y=chl_zoox_pg, x=treatment, fill = genotype)) + 
  geom_boxplot() + 
  theme_classic()
```

```{r}

#Checking non logged transformed chl_zoox_pg data
ggdensity(data$chl_zoox_pg, 
          main = "Density plot of chl/zoox",
          xlab = "chl/zoox (pg) of coral")
#SKEWED
ggqqplot(data$chl_zoox_pg)
shapiro.test(data$chl_zoox_pg)
#3.813e=6 

#logdata
data$logchl_zoox_pg<-log(data$chl_zoox_pg+1)

ggdensity(data$logchl_zoox_pg, 
          main = "Density plot of Chl:zoox",
          xlab = "Chl:zoox content")
#SKEWED
ggqqplot(data$logchl_zoox_pg)
shapiro.test(data$logchl_zoox_pg)
#0.6546
bartlett.test(logchl_zoox_pg~interaction(treatment,genotype), data=data)
bartlett.test(logchl_zoox_pg~treatment, data=data)
bartlett.test(logchl_zoox_pg~genotype, data=data)
leveneTest(logchl_zoox_pg~treatment, data=data)
leveneTest(logchl_zoox_pg~genotype, data=data)
leveneTest(logchl_zoox_pg ~ treatment*genotype, data = data)
fligner.test(logchl_zoox_pg~treatment, data=data)
fligner.test(logchl_zoox_pg~genotype, data=data)
# #equal variance and normal data whhen logged- 
#equal variance ANOVA/lm
```

Parametric test ANOVA lm

```{r}
chzoosum<-data %>% 
  group_by(genotype,treatment) %>%
  get_summary_stats(logchl_zoox_pg, type = "common")

chzoosumT<-kable(chzoosum, digits = 4,
      caption = "Summary statistics for Log Zoox/protein densities",
      col.names = c("Treatment", "Genotype", "Parameter", "n", "Min", "Max", "Median", "IQR", "Mean","SD", "SE", "CI"),
      align = 'c') %>%
  kable_styling(bootstrap_options =
                  c("hover", "responsive", "striped"),
                full_width = F, position = "center")

chzoosumT

# Proceed with ANOVA/lm post hoc Tukeys HSD for logged zooxanthellae
LchlPmoda<-aov(logchl_zoox_pg~genotype*treatment,data)
summary(LchlPmoda)
#treat
#treatment diff 0.00776
#genotype diff 0.03120
pairwise.t.test(data$logchl_zoox_pg, data$treatment,
                p.adjust.method = "bonf")
#1 & 2 0.027 
#2 & C 0.014


pairwise.t.test(data$logchl_zoox_pg, data$genotype,
                p.adjust.method = "bonf")
#NA

pairwise.t.test(data$logchl_zoox_pg,data$cat,
                p.adjust.method = "bonf")

#T1M6:T2K2- 0.019

#more
TukeyHSD(LchlPmoda)

#K2:T2-M6:T1  1.612648919  0.0133628
LchlPtSSt = summarySE(data, measurevar="logchl_zoox_pg",
                     groupvars=c("treatment"))

LchlPtSSt
LchlPgSSt = summarySE(data, measurevar="logchl_zoox_pg",
                     groupvars=c("genotype"))

LchlPgSSt
LchlPiSSt = summarySE(data, measurevar="logchl_zoox_pg",
                     groupvars=c("cat"))

LchlPiSSt
 
LchlPtbar<-ggplot(LchlPtSSt, aes(x=factor(treatment), y=logchl_zoox_pg, fill=treatment)) + 
    geom_bar(stat="identity", width=0.8) +
    geom_errorbar(aes(ymin=logchl_zoox_pg-se, ymax=logchl_zoox_pg+se),
                  width=.2) +
    xlab("Treatment") +
  ylab(expression(paste("log", O[2], mu,"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle('Logc')+
   theme_classic()+
    scale_x_discrete(breaks=c("T1", "T2", "T3", "TC"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))
 LchlPtbar
  
LchlPImod<-lm(logchl_zoox_pg~genotype*treatment,data)
summary(LchlPImod)
# F- 2.224, DF- 36 p-value 0.03511**
LchlPtmod<-aov(logchl_zoox_pg~treatment,data)
summary(LchlPtmod)
# treat df 3 F 4.369 P= 0.00889 
TukeyHSD(LchlPtmod)
#T1:T2- 0.0223825
#T2:Tc- 0.0119583
LchlPgmod<-aov(logchl_zoox_pg~genotype,data)
summary(LchlPgmod)
#df 2 F 3.258 p= 0.0477
TukeyHSD(LchlPgmod)
#NA 0.0617 M6-K2

LchlPImodP<-ggplot(LchlPImod, aes(x=treatment, logchl_zoox_pg, fill= genotype))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('Treatment')+
  ylab(expression(paste(O[2], mu,"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Log  Chlorophyll/zoo")+
  stat_compare_means(label.y=4.5, method = "anova")+
  scale_fill_manual(values = c('red','green4', 'blue'))+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))
LchlPImodP

ggexport(LchlPImodP, filename = "LchlPANOplotinter.pdf")


LchlPgmodP<-ggplot(LchlPgmod, aes(x=genotype, logchl_zoox_pg, fill= genotype))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('Genotype')+
  ylab(expression(paste(O[2], mu,"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Log  Chlorophyll/zoo")+
    stat_summary(fun.y=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  stat_compare_means(label.y=4.5, method = "anova")+
  scale_fill_manual(values = c('red','green4', 'blue'))
LchlPgmodP

ggexport(LchlPgmodP, filename = "LchlPANOplotgeno.pdf")

LchlPtmodP<-ggplot(LchlPtmod, aes(x=treatment, logchl_zoox_pg, fill= treatment))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1),outlier.shape=1)+
  theme_classic()+
  xlab('Treatment')+
  ylab(expression(paste(O[2], mu,"mol cm"^{-2}, "hr"^{-1})))+
  ggtitle("Log  Chlorophyll/zoo")+
      stat_summary(fun.y=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  stat_compare_means(label.y=4.5, method = "anova")+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))

LchlPtmodP
ggexport(LchlPtmodP, filename = "LchlPANOplotrea.pdf")

stat.testi<-aov(logchl_zoox_pg~treatment,data)%>%
  tukey_hsd()

LchlPgmodPTu<-ggboxplot(data, x = "treatment", y = "logchl_zoox_pg", fill= "treatment")+
  stat_pvalue_manual(
    stat.testi, label = "p.adj", 
    y.position = c(4,5,6,6.5,7,8))

plotczp<-LchlPgmodPTu+
    scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))
plotczp
ggexport(plotczp, filename = "LchlPANOplottreaTUK.pdf")

stat.testi<-aov(logchl_zoox_pg~genotype,data)%>%
  tukey_hsd()

LchlPgmodPTug<-ggboxplot(data, x = "genotype", y = "logchl_zoox_pg", fill= "genotype")+
  stat_pvalue_manual(
    stat.testi, label = "p.adj", 
    y.position = c(4,5,6))

plotczpg<-LchlPgmodPTug+
    scale_fill_manual(values = c('red','green4', 'blue'))
plotczpg
ggexport(plotczpg, filename = "LchlPANOplotgenoTUK.pdf")
```


Chl/protein
```{r}
ggplot(data, aes(y=chl_protein, x=treatment, fill = genotype)) + 
  geom_boxplot() + 
  theme_classic()
```

```{r}

#Checking non logged transformed chl_protein data
ggdensity(data$chl_protein, 
          main = "Density plot of chl_protein",
          xlab = "chl_protein of coral")
#SKEWED
ggqqplot(data$chl_protein)
shapiro.test(data$chl_protein)
#3.419e-5 
#logdata
data$logchl_protein<-log(data$chl_protein+1)

ggdensity(data$logchl_protein, 
          main = "Density plot of Chl:protein",
          xlab = "Chl:Protein content")
#SKEWED
ggqqplot(data$logchl_protein)
shapiro.test(data$logchl_protein)
#0.07968
bartlett.test(logchl_protein~interaction(treatment,genotype), data=data)
#0.007
bartlett.test(logchl_protein~treatment, data=data)
#0.04551
bartlett.test(logchl_protein~genotype, data=data)
#0.01166
leveneTest(logchl_protein~treatment, data=data)
leveneTest(logchl_protein~genotype, data=data)
#0.0397
leveneTest(logchl_protein ~ treatment*genotype, data = data)
#4.39e-5
fligner.test(logchl_protein~treatment, data=data)
fligner.test(logchl_protein~genotype, data=data)
# the variance (and thus standard deviations) of the groups differ significantly DO NOT USE
#logit transformation
data$logitchl_protein<-logit(data$chl_protein)

ggdensity(data$logitchl_protein, 
          main = "Density plot of Chl:protein",
          xlab = "Protein content")
#SKEWED
ggqqplot(data$logitchl_protein)
shapiro.test(data$logitchl_protein)
#0.5466
bartlett.test(logitchl_protein~interaction(treatment,genotype), data=data)
#0.0104
bartlett.test(logitchl_protein~treatment, data=data)
bartlett.test(logitchl_protein~genotype, data=data)
#0.03649
leveneTest(logitchl_protein~treatment, data=data)
leveneTest(logitchl_protein~genotype, data=data)
leveneTest(logitchl_protein ~ treatment*genotype, data = data)
#0.0001296
fligner.test(logitchl_protein~treatment, data=data)
fligner.test(logitchl_protein~genotype, data=data)
#Non-parametric testing for Chl:protein, sample variance is not the same between the populations 

# data failed Bartlett & Levenes test for homogeneity  #non-parameteric test below

# USE NON PARAMETRIC TESTS FOR CHLOROPHYLL:PROTEIN
#Kruskal Wallis kruskal.test(y~x) y is continuous, x is categorical
```

Non parametric Kruskal Wallis
```{r}
data %>% 
  group_by(genotype,treatment) %>%
  get_summary_stats(chl_protein, type = "common")

#box plot
ggboxplot(data, x = "treatment", y = "chl_protein")
ggboxplot(data, x = "genotype", y = "chl_protein")

res.kruskal <- data %>% kruskal_test(chl_protein ~ treatment)
res.kruskal

res.kruskal2 <- data %>% kruskal_test(chl_protein ~ genotype)
res.kruskal2
#0.0134

#EFFECT SIZE
data %>% kruskal_effsize(chl_protein ~ treatment)
# -0.0349-- small
data %>% kruskal_effsize(chl_protein ~ genotype)
# 0.147- large
# Pairwise comparisons
pwc <- data %>% 
  dunn_test(chl_protein ~ treatment, p.adjust.method = "BH") 
pwc
#NA no differences
pwcg <- data %>% 
  dunn_test(chl_protein ~ genotype, p.adjust.method = "BH") 
pwcg
#K2:M6- 0.0110
pwc <- pwc %>% add_xy_position(x = "treatment")
pwcg <- pwcg %>% add_xy_position(x = "genotype")

mod<-lm(chl_protein~treatment*genotype,data)

effects::allEffects(mod)
summary(mod)
#F 1.302 df 36 p-value- 02631
res.kruskalD <- data %>% kruskal_test(chl_protein ~ cat)
res.kruskalD
# stat 14.3 df 11 p-value 0.216
#EFFECT SIZE
data %>% kruskal_effsize(chl_protein ~ cat)
# 0.0921 -moderate
dunn.test(data$chl_protein, data$cat, method="BH")
#chi-squared = 14.3163, df = 11, p-value = 0.2
pwcD <- data %>% 
  dunn_test(chl_protein ~ cat, p.adjust.method = "BH") 
pwcD
pwcD <- pwcD %>% add_xy_position(x = "cat")


ChloProplotT<-ggboxplot(data, x = "treatment", y = "chl_protein", color= "black", fill="treatment", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab('Chlorophyll/Protein')+
  xlab('Treatment')+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
  stat_summary(fun.y=mean, geom="point", size=2)+ #line is median, and closed circle is mean
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))+
   stat_pvalue_manual(pwc, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.kruskal, detailed = TRUE),
    caption = get_pwc_label(pwc)
    )

ChloProplotT
ggexport(ChloProplotT, filename = "ChloProplotT.pdf")


ChloProplotG<-ggboxplot(data, x = "genotype", y = "chl_protein", color= "black", fill="genotype", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab('Chlorophyll/Protein')+
  xlab('Genotype')+
  scale_fill_manual(values = c('red','green4', 'blue'))+
  stat_summary(fun.y=mean, geom="point", size=2)+ #line is median, and closed circle is mean
   stat_pvalue_manual(pwcg, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.kruskal2, detailed = TRUE),
    caption = get_pwc_label(pwcg)
    )

ChloProplotG
ggexport(ChloProplotG, filename = "ChloProplotG.pdf")


ChloProplotI<-ggboxplot(data, x = "cat", y = "chl_protein", color= "black", fill="genotype", outlier.shape = 1) +
  stat_boxplot(geom='errorbar', linetype=1, width=0.5)+  #whiskers
  ylab('Chlorophyll/Protein')+
  xlab('')+
  ggtitle('')+
  scale_fill_manual(values = c('red','green4', 'blue'))+
  stat_summary(fun.y=mean, geom="point", size=2)+ #line is median, and closed circle is mean
   stat_pvalue_manual(pwcD, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.kruskalD, detailed = TRUE),
    caption = get_pwc_label(pwcD)
    )
ChloProplotI

ggexport(ChloProplotI, filename = "ChloProplotI.pdf")


ggboxplot(data, x = "treatment", y = "chl_protein", color= "black", fill="genotype", outlier.shape = 1) +
  ylab('Total Chlorophyll/Protein')+
  xlab('Treatment')+
  scale_fill_manual(values = c('red','green4', 'blue'))+
  stat_summary(fun.y=mean, geom="point", size=2)+
  scale_x_discrete(breaks=c("T1", "T2", "T3", "Tc"),
        labels=c("Sprinkler", "Feeding", "Interactive","Control"))

ggboxplot(data, x = "genotype", y = "chl_protein", color= "black", fill="treatment", outlier.shape = 1) +
  ylab('Total Chlorophyll/Protein')+
  xlab('Genotype')+
  scale_fill_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))
```


```{r}
#write.csv(data,"C:/Github/TPC_Acropora/R_output_Data_Frames/EcophysLOGGEDdata.csv")

```
