---
title: "Coral Holobiont Physiology under ramping temperature exposure"
output: 
  html_document:
    theme: simplex
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

<style>
  h2{color: teal !important}
  h1{color: navy !important}
  body{background-color: gray95 !important}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(warn = -1)
```

```{r packages, include=FALSE}
setwd("C:/Github/TPC_Acropora")
#library("devtools")
#install_github("vqv/ggbiplot") # need this to download ggbiplot if not already installed
## Packages to load
library(devtools)
#install_github("vqv/ggbiplot")
#library(ggbiplot)
#require(devtools)
library(usethis)
#library(install_version)
library(magrittr)
#install_version("Magritter", version = "	2.0.1", repos = "http://cran.us.r-project.org")
library(knitr)
library(readr)
library(ggplot2)
library(dplyr)
#library(ggbiplot)
library(tidyr)
#library(openxlsx)
library(plotly)
library(tidyverse)
library(vegan)
library(shiny)
library(Rmisc)
library(cowplot)
library(ggfortify)
library(kableExtra)
library(readr)
#library(lmerTest)
library(vroom)
library(ggpubr)
library(magick)
library(Hmisc)
library(corrplot)
library(grid)
library(gridGraphics)
library(performance)
library(MASS)
```

```{r set formatting and labels, include=FALSE}
## Set some standards and units
# dodge width
#dodge=position_dodge(width=0.3)
#dodge2=position_dodge(width = 0.6)
#jitter=position_jitter(width=0.1)
# set figure theme
theme_set(theme_classic())
# set parameter labels
Tlab<-"Temperature (°C)"
plab<-expression(paste("Total protein ( "*mu,"g cm"^-2,")"))
dlab<-expression(paste("Cell density (10"^5,"cells cm"^-2,")"))
glab<-expression(paste("Growth Rate (%)"))
clab<-expression(paste("Chlorophyll a ( "*mu,"g cm"^-2,")"))
# set the current date
date <- Sys.Date() 
```

```{r original dataframe adjustment, include=FALSE}
df <- read_csv("C:/Github/TPC_Acropora/R_output_Data_Frames/EcophysLOGGEDdata.csv")
# read in full dataframe
# remove unnecessary column
df$X1 <- NULL
# set columns as factors
df$cat <- as.factor(df$cat)
df$genotype <- as.factor(df$genotype)
df$coral_id <- as.factor(df$coral_id)
df$treatment <- as.factor(df$treatment) 
# select columns of interest only
df2 <- df[,c(1:3,5,11, 19,22, 23)] 
df2 <- gather(df2, param, value, protein_3d_ug_cm2,chl_ug,percent_growth,totzoox) # make column of parameter and value
```


```{r}
# select columns of interest only for ALL logged parameters
dfl <- df[,c(1:3, 20, 22, 24:26)]
dfl <- gather(dfl, param, value, logprotein, logzoo, logpercent_growth, logchl_ug_cm2) # make column of parameter and value
```

```{r}
# subset the dataframe for only T0 samples (inital)
data<-read.csv("C:/Github/TPC_Acropora/Raw_data/Ecophys_data/TidyEcopphysData.csv")
data <- janitor::clean_names(data)

df_i<-data%>%
  filter(treatment=="i")%>%
  filter(genotype!="M7")

df_i$totzoox<-df_i$zoox_cm2_3d/100000

df_i$logzoo<-log(df_i$totzoox+1)
df_i$logprotein<-log(df_i$protein_3d_ug_cm2+1)
df_i$logchl_ug_cm2<-log(df_i$chl_ug_cm2+1)

df_i$cat <- paste(df_i$treatment,df_i$genotype)
df_i$cat<-factor(df_i$cat)
df_i$genotype <- as.factor(df_i$genotype)
df_i$coral_id <- as.factor(df_i$coral_id)
df_i$treatment <- as.factor(df_i$treatment) 

df_iT0l <-df_i[,c(1:3, 21:24)]

df_iT0 <- df_i[,c(1:3,5,15,20,24)]

df_il <- gather(df_iT0l, param, value, logprotein, logzoo,  logchl_ug_cm2)
df_i2 <- gather(df_iT0, param, value, protein_3d_ug_cm2, totzoox,  chl_ug_cm2)
# set up the dataframe
df_sp<-df[,c(1:3, 5,15, 22,24:25)]

data.table::setnames(df_sp, old = c('protein_3d_ug_cm2','chl_ug_cm2', 'logpercent_growth', 'logzoo'), new = c('Pro','Chlo','Growth','Zoox'))

df_sp <- unique(df_sp)# remove any duplicate rows
ldf_sp <- gather(df_sp, param, value, c(4:5, 7:8))
```

```{r bootstrap model setup}
## Function to remove rows with any missing values
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}
## Performing the parametric bootstrapping of the model:
bootnum = 2000 # set number of iterations (we used 2000) between 999 and 9999
seed = 7 #seed to make results replicatable (our seed was 7)
```


## Model selection for physiology{.tabset}

Physiological response parameters were assessed using mixed-effects linear models across species and treatments. Model selection was carried out using backward elimination of random-effects followed by fixed-effects using the package [*lmerTest*](https://cran.r-project.org/web/packages/lmerTest/lmerTest.pdf) (version `r packageVersion("lmerTest")`)



```{r T0 model selection, eval=FALSE, include=FALSE}
### Planning to model all measured values in response to parameter and genotype
df_fin <- (df2) 
df_finl<-(dfl)
## running forloop to model each per genotype in each parameter
param_list <- levels(factor(df_fin$param))# create a list of parameter names
for (p in 1:length(param_list)) {
  
  # subset T0 dataframe by selected param name
  param_name <- param_list[p]
  T0_df_sub <- subset(df_fin, param == param_name)
  
  # run linear model 
  model <- lm(value ~ genotype, data = T0_df_sub) 
  out <- simulate(model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model response 2000 (bootnum)   times
  boots <- apply(out, 2, function(x) predict(lm(x ~ genotype, data = T0_df_sub), re.form=NA)) #   applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
  boots <- cbind(predict(model, re.form = NA), boots) # adds column to above df of predicted values without   random effects
  df_fin_a <- (cbind(T0_df_sub, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) #   apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual   values dataframe
  colnames(df_fin_a)[7:9] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values
  ## save model results
  T0_df <- paste("LMER_model_outputs/Genotype_models/lm", param_name, date, sep="_") 
  T0_df <- paste(T0_df, ".csv", sep="") 
  write.csv(df_fin_a, file = T0_df)  # last saved model was: 2020-11-11
  
  }
## read in all T0 model files and merge into single file
files <- fs::dir_ls(glob = "*csv", path = "LMER_model_outputs/Genotype_models")
mergedT0 <- vroom(files)
write.csv(mergedT0, file = paste("LMER_model_outputs/Genotype_models/Genotype_combined_out_", date, ".csv", sep=""))  # last saved model was: 2021-3-23  
```


```{r}
#For logged
## running forloop to model each T0 CI per species in each parameter
param_list <- levels(factor(df_finl$param))# create a list of parameter names
for (p in 1:length(param_list)) {
  
  # subset T0 dataframe by selected param name
  param_name <- param_list[p]
  T0_dfl_sub <- subset(df_finl, param == param_name)
  
  # run linear model 
  model <- lm(value ~ genotype, data = T0_dfl_sub) 
  out <- simulate(model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model response 2000 (bootnum)   times
  boots <- apply(out, 2, function(x) predict(lm(x ~ genotype, data = T0_dfl_sub), re.form=NA)) #   applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
  boots <- cbind(predict(model, re.form = NA), boots) # adds column to above df of predicted values without   random effects
  df_fin_al <- (cbind(T0_dfl_sub, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) #   apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual   values dataframe
  colnames(df_fin_al)[7:9] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values
  ## save model results
  T0_dfl <- paste("LMER_model_outputs/Genotype_models/log/lm", param_name, date, sep="_") 
  T0_dfl <- paste(T0_dfl, ".csv", sep="") 
  write.csv(df_fin_al, file = T0_dfl)  # last saved model was: 2020-11-11
  
  }
## read in all T0 model files and merge into single file
files <- fs::dir_ls(glob = "*csv", path = "LMER_model_outputs/Genotype_models/log")
mergedT0 <- vroom(files)
write.csv(mergedT0, file = paste("LMER_model_outputs/Genotype_models/log/Genotypelog_combined_out_", date, ".csv", sep=""))  # last saved model was: 2021-3-23
```

Treatment linear models
```{r}
## running forloop to model each per treatment in each parameter
param_list <- levels(factor(df_fin$param))# create a list of parameter names
for (p in 1:length(param_list)) {
  
  # subset T0 dataframe by selected param name
  param_name <- param_list[p]
  T0_df_sub <- subset(df_fin, param == param_name)
  
  # run linear model 
  model <- lm(value ~ treatment, data = T0_df_sub) 
  out <- simulate(model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model response 2000 (bootnum)   times
  boots <- apply(out, 2, function(x) predict(lm(x ~ treatment, data = T0_df_sub), re.form=NA)) #   applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
  boots <- cbind(predict(model, re.form = NA), boots) # adds column to above df of predicted values without   random effects
  df_fin_a <- (cbind(T0_df_sub, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) #   apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual   values dataframe
  colnames(df_fin_a)[7:9] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values
  ## save model results
  T0_df <- paste("LMER_model_outputs/Treatment_models/lm", param_name, date, sep="_") 
  T0_df <- paste(T0_df, ".csv", sep="") 
  write.csv(df_fin_a, file = T0_df)  # last saved model was: 2020-11-11
  
  }
## read in all T0 model files and merge into single file
files <- fs::dir_ls(glob = "*csv", path = "LMER_model_outputs/Treatment_models")
mergedT0 <- vroom(files)
write.csv(mergedT0, file = paste("LMER_model_outputs/Treatment_models/Treatment_combined_out_", date, ".csv", sep=""))  # last saved model was: 2021-3-23  
```


```{r}
#For logged
## running forloop to model each T0 CI per species in each parameter
param_list <- levels(factor(df_finl$param))# create a list of parameter names
for (p in 1:length(param_list)) {
  
  # subset T0 dataframe by selected param name
  param_name <- param_list[p]
  T0_dfl_sub <- subset(df_finl, param == param_name)
  
  # run linear model 
  model <- lm(value ~ treatment, data = T0_dfl_sub) 
  out <- simulate(model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model response 2000 (bootnum)   times
  boots <- apply(out, 2, function(x) predict(lm(x ~ treatment, data = T0_dfl_sub), re.form=NA)) #   applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
  boots <- cbind(predict(model, re.form = NA), boots) # adds column to above df of predicted values without   random effects
  df_fin_al <- (cbind(T0_dfl_sub, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) #   apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual   values dataframe
  colnames(df_fin_al)[7:9] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values
  ## save model results
  T0_dfl <- paste("LMER_model_outputs/Treatment_models/log/lm", param_name, date, sep="_") 
  T0_dfl <- paste(T0_dfl, ".csv", sep="") 
  write.csv(df_fin_al, file = T0_dfl)  # last saved model was: 2020-11-11
  
  }
## read in all T0 model files and merge into single file
files <- fs::dir_ls(glob = "*csv", path = "LMER_model_outputs/Treatment_models/log")
mergedT0 <- vroom(files)
write.csv(mergedT0, file = paste("LMER_model_outputs/Treatment_models/log/Treatmentlog_combined_out_", date, ".csv", sep=""))  # last saved model was: 2021-3-23
```


SP data modelling
```{r}
### Planning to model all measured values in response to parameter and treatment
ldf_sp
## running forloop to model each per treatment in each parameter
param_list <- levels(factor(ldf_sp$param))# create a list of parameter names
for (p in 1:length(param_list)) {
  
  # subset T0 dataframe by selected param name
  param_name <- param_list[p]
  T0_df_sub <- subset(ldf_sp, param == param_name)
  
  # run linear model 
  model <- lm(value ~ treatment, data = T0_df_sub) 
  out <- simulate(model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model response 2000 (bootnum)   times
  boots <- apply(out, 2, function(x) predict(lm(x ~ treatment, data = T0_df_sub), re.form=NA)) #   applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
  boots <- cbind(predict(model, re.form = NA), boots) # adds column to above df of predicted values without   random effects
  df_fin_a <- (cbind(T0_df_sub, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) #   apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual   values dataframe
  colnames(df_fin_a)[7:9] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values
  ## save model results
  T0_df <- paste("LMER_model_outputs/SP/Treatment/lm", param_name, date, sep="_") 
  T0_df <- paste(T0_df, ".csv", sep="") 
  write.csv(df_fin_a, file = T0_df)  # last saved model was: 2020-11-11
  
  }
## read in all T0 model files and merge into single file
files <- fs::dir_ls(glob = "*csv", path = "LMER_model_outputs/SP/Treatment")
mergedT0 <- vroom(files)
write.csv(mergedT0, file = paste("LMER_model_outputs/SP/Treatment/Treatment_combined_out_", date, ".csv", sep=""))  # last saved model was: 2021-3-23
```

Genotype
```{r}
### Planning to model all measured values in response to parameter and Genotype
ldf_sp
## running forloop to model each per Genotype in each parameter
param_list <- levels(factor(ldf_sp$param))# create a list of parameter names
for (p in 1:length(param_list)) {
  
  # subset T0 dataframe by selected param name
  param_name <- param_list[p]
  T0_df_sub <- subset(ldf_sp, param == param_name)
  
  # run linear model 
  model <- lm(value ~ genotype, data = T0_df_sub) 
  out <- simulate(model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model response 2000 (bootnum)   times
  boots <- apply(out, 2, function(x) predict(lm(x ~ genotype, data = T0_df_sub), re.form=NA)) #   applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
  boots <- cbind(predict(model, re.form = NA), boots) # adds column to above df of predicted values without   random effects
  df_fin_a <- (cbind(T0_df_sub, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) #   apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual   values dataframe
  colnames(df_fin_a)[7:9] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values
  ## save model results
  T0_df <- paste("LMER_model_outputs/SP/Genotype/lm", param_name, date, sep="_") 
  T0_df <- paste(T0_df, ".csv", sep="") 
  write.csv(df_fin_a, file = T0_df)  # last saved model was: 2020-11-11
  
  }
## read in all T0 model files and merge into single file
files <- fs::dir_ls(glob = "*csv", path = "LMER_model_outputs/SP/Genotype")
mergedT0 <- vroom(files)
write.csv(mergedT0, file = paste("LMER_model_outputs/SP/Genotype/Genotype_combined_out_", date, ".csv", sep=""))  # last saved model was: 2021-3-23
```


Interctive Cat

```{r}
### Planning to model all measured values in response to parameter and Genotype
ldf_sp
## running forloop to model each per Genotype in each parameter
param_list <- levels(factor(ldf_sp$param))# create a list of parameter names
for (p in 1:length(param_list)) {
  
  # subset T0 dataframe by selected param name
  param_name <- param_list[p]
  T0_df_sub <- subset(ldf_sp, param == param_name)
  
  # run linear model 
  model <- lm(value ~ cat, data = T0_df_sub) 
  out <- simulate(model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model response 2000 (bootnum)   times
  boots <- apply(out, 2, function(x) predict(lm(x ~ cat, data = T0_df_sub), re.form=NA)) #   applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
  boots <- cbind(predict(model, re.form = NA), boots) # adds column to above df of predicted values without   random effects
  df_fin_a <- (cbind(T0_df_sub, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) #   apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual   values dataframe
  colnames(df_fin_a)[7:9] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values
  ## save model results
  T0_df <- paste("LMER_model_outputs/SP/CAT/lm", param_name, date, sep="_") 
  T0_df <- paste(T0_df, ".csv", sep="") 
  write.csv(df_fin_a, file = T0_df)  # last saved model was: 2020-11-11
  
  }
## read in all T0 model files and merge into single file
files <- fs::dir_ls(glob = "*csv", path = "LMER_model_outputs/SP/CAT")
mergedT0 <- vroom(files)
write.csv(mergedT0, file = paste("LMER_model_outputs/SP/CAT/CAT_combined_out_", date, ".csv", sep=""))  # last saved model was: 2021-3-23
```

Cat linear models
```{r}
## running forloop to model each per treatment in each parameter
param_list <- levels(factor(df_fin$param))# create a list of parameter names
for (p in 1:length(param_list)) {
  
  # subset T0 dataframe by selected param name
  param_name <- param_list[p]
  T0_df_sub <- subset(df_fin, param == param_name)
  
  # run linear model 
  model <- lm(value ~ cat, data = T0_df_sub) 
  out <- simulate(model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model response 2000 (bootnum)   times
  boots <- apply(out, 2, function(x) predict(lm(x ~ cat, data = T0_df_sub), re.form=NA)) #   applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
  boots <- cbind(predict(model, re.form = NA), boots) # adds column to above df of predicted values without   random effects
  df_fin_a <- (cbind(T0_df_sub, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) #   apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual   values dataframe
  colnames(df_fin_a)[7:9] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values
  ## save model results
  T0_df <- paste("LMER_model_outputs/Cat_models/lm", param_name, date, sep="_") 
  T0_df <- paste(T0_df, ".csv", sep="") 
  write.csv(df_fin_a, file = T0_df)  # last saved model was: 2020-11-11
  
  }
## read in all T0 model files and merge into single file
files <- fs::dir_ls(glob = "*csv", path = "LMER_model_outputs/Cat_models")
mergedT0 <- vroom(files)
write.csv(mergedT0, file = paste("LMER_model_outputs/Cat_models/Cat_combined_out_", date, ".csv", sep=""))  # last saved model was: 2021-3-23  
```

```{r}
#For logged
## running forloop to model each T0 CI per species in each parameter
param_list <- levels(factor(df_finl$param))# create a list of parameter names
for (p in 1:length(param_list)) {
  
  # subset T0 dataframe by selected param name
  param_name <- param_list[p]
  T0_dfl_sub <- subset(df_finl, param == param_name)
  
  # run linear model 
  model <- lm(value ~ cat, data = T0_dfl_sub) 
  out <- simulate(model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model response 2000 (bootnum)   times
  boots <- apply(out, 2, function(x) predict(lm(x ~ cat, data = T0_dfl_sub), re.form=NA)) #   applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
  boots <- cbind(predict(model, re.form = NA), boots) # adds column to above df of predicted values without   random effects
  df_fin_al <- (cbind(T0_dfl_sub, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) #   apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual   values dataframe
  colnames(df_fin_al)[7:9] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values
  ## save model results
  T0_dfl <- paste("LMER_model_outputs/Cat_models/log/lm", param_name, date, sep="_") 
  T0_dfl <- paste(T0_dfl, ".csv", sep="") 
  write.csv(df_fin_al, file = T0_dfl)  # last saved model was: 2020-11-11
  
  }
## read in all T0 model files and merge into single file
files <- fs::dir_ls(glob = "*csv", path = "LMER_model_outputs/Cat_models/log")
mergedT0 <- vroom(files)
write.csv(mergedT0, file = paste("LMER_model_outputs/Cat_models/log/catlog_combined_out_", date, ".csv", sep=""))  # last saved model was: 2021-3-23
```


<br/>


## Correlation assessments{.tabset}

Here, I am exploring the relationships between each physiology parameter measured above.

```{r T90 df setup}
#protein_3d_ug_cm2,chl_ug,percent_growth,totzoox

df_90 <- df 
df_90 <- df_90[,c(1:3,5,15, 19,22, 23)]
df_90 <- completeFun(df_90, "protein_3d_ug_cm2")
df_90 <- completeFun(df_90, "totzoox")
df_90 <- completeFun(df_90, "chl_ug_cm2")
df_90 <- completeFun(df_90, "percent_growth")
df_90_l <- gather(df_90, param, value, c(4:6, 8))

```

```{r}
#logprotein, logzoo, logpercent_growth, logchl_ug_cm2
df_90l <- df 
df_90l <- df_90l[,c(1:3, 20, 22, 24:26)]
df_90l <- completeFun(df_90l, "logprotein")
df_90l <- completeFun(df_90l, "logzoo")
df_90l <- completeFun(df_90l, "logchl_ug_cm2")
df_90l <- completeFun(df_90l, "logpercent_growth")
df_90l_l <- gather(df_90l, param, value, c(4,6:8))
```

```{r}
df_iT0l
df_iT0 

df_90
df_90l

```

```{r correlation df setup}
## dataframe updates
df_90$ID <- paste(df_90$coral_id, df_90$treatment, sep = "_") # add coral name to treatment
df_subset <- as.data.frame(df_90) # subset the df for desired columns
df_subset <- df_90[!duplicated(df_90$ID), ] # remove any duplicated values NO Duplicates
rownames(df_subset) <- df_subset$ID # rename rows with ID
## dataframe updates log
df_90l$ID <- paste(df_90l$coral_id, df_90l$treatment, sep = "_") # add coral name to treatment
df_subsetl <- as.data.frame(df_90l) # subset the df for desired columns
df_subsetl <- df_90l[!duplicated(df_90l$ID), ] # remove any duplicated values NO Duplicates
rownames(df_subsetl) <- df_subsetl$ID # rename rows with ID

data.table::setnames(df_90, old = c('protein_3d_ug_cm2','chl_ug_cm2', 'percent_growth', 'totzoox'), new = c('Pro','Chlo','Growth','Zoox'))
df_90

data.table::setnames(df_90l, old = c('logprotein','logchl_ug_cm2', 'logpercent_growth', 'logzoo'), new = c('LPro','LChlo','LGrowth','LZoox'))
df_90l
## dataframe updates
df_iT0$ID <- paste(df_iT0$coral_id, df_iT0$treatment, sep = "_") # add coral name to treatment
df_subseti <- as.data.frame(df_iT0) # subset the df for desired columns
df_subseti <- df_iT0[!duplicated(df_iT0$ID), ] # remove any duplicated values NO Duplicates
rownames(df_subseti) <- df_subseti$ID # rename rows with ID
## dataframe updates log
df_iT0l$ID <- paste(df_iT0l$coral_id, df_iT0l$treatment, sep = "_") # add coral name to treatment
df_subsetil <- as.data.frame(df_iT0l) # subset the df for desired columns
df_subseitl <- df_iT0l[!duplicated(df_iT0l$ID), ] # remove any duplicated values NO Duplicates
rownames(df_subsetil) <- df_subsetil$ID # rename rows with ID


data.table::setnames(df_iT0, old = c('protein_3d_ug_cm2','chl_ug_cm2',  'totzoox'), new = c('Pro','Chlo','Zoox'))
df_iT0
data.table::setnames(df_iT0l, old = c('logprotein','logchl_ug_cm2', 'logzoo'), new = c('LPro','LChlo','LZoox'))
df_iT0l




df_90lng<-df_90l
df_90lng$LGrowth=NULL
df_pcal<-rbind(df_90lng,df_iT0l)

df_90ng<-df_90
df_90ng$Growth=NULL
df_pca<-rbind(df_90ng,df_iT0)



df_pca
df_pcal
##
##run anovas etc
```


```{r}
acph.pca <- prcomp(df_subset[,c(4:6,8)], center = TRUE,scale. = TRUE)
summary(acph.pca)
str(acph.pca)
autoplot(acph.pca)
ta<-autoplot(acph.pca, data = df_subset, colour = 'treatment')
a<-autoplot(acph.pca, data = df_subset, colour = 'genotype')
autoplot(acph.pca, data = df_subset, colour = 'cat')


acph.pcal <- prcomp(df_subsetl[,c(4,6:8)], center = TRUE,scale. = TRUE)
summary(acph.pcal)
str(acph.pcal)
autoplot(acph.pcal)
lta<-autoplot(acph.pcal, data = df_subsetl, colour = 'treatment')
b<-autoplot(acph.pcal, data = df_subsetl, colour = 'genotype')
autoplot(acph.pcal, data = df_subsetl, colour = 'cat')

acph.pcai <- prcomp(df_subseti[,c(4:6)], center = TRUE,scale. = TRUE)
summary(acph.pcai)
str(acph.pcai)
autoplot(acph.pcai)
ita<-autoplot(acph.pcai, data = df_subseti, colour = 'treatment')
c<-autoplot(acph.pcai, data = df_subseti, colour = 'genotype')
autoplot(acph.pcai, data = df_subseti, colour = 'cat')

acph.pcail <- prcomp(df_subsetil[,c(4:6)], center = TRUE,scale. = TRUE)
summary(acph.pcail)
str(acph.pcail)
autoplot(acph.pcail)
ilta<-autoplot(acph.pcail, data = df_subsetil, colour = 'treatment')
d<-autoplot(acph.pcail, data = df_subsetil, colour = 'genotype')
autoplot(acph.pcail, data = df_subsetil, colour = 'cat')


acph.pcaa <- prcomp(df_pca[,c(4,5,7)], center = TRUE,scale. = TRUE)
summary(acph.pcaa)
str(acph.pcaa)
autoplot(acph.pcaa)
ata<-autoplot(acph.pcaa, data =df_pca, colour = 'treatment')
e<-autoplot(acph.pcaa, data =df_pca, colour = 'genotype')
autoplot(acph.pcaa, data =df_pca, colour = 'cat')


acph.pcaal <- prcomp(df_pcal[,c(4,6,7)], center = TRUE,scale. = TRUE)
summary(acph.pcaal)
str(acph.pcaal)
autoplot(acph.pcaal)
atal<-autoplot(acph.pcaal, data =df_pcal, colour = 'treatment')
f<-autoplot(acph.pcaal, data =df_pcal, colour = 'genotype')
autoplot(acph.pcaal, data =df_pcal, colour = 'cat')


plot_grid(ta,lta,ita,ilta,ata,atal)
plot_grid(a,b,c,d,e,f)

```


```{r}
#Joing tables

CAP <- df[,c(1:3,5,15, 22, 23)]
CAPi<-df_i[,c(1:3,5,15,20, 24)]
Cpa<-rbind(CAP,CAPi)

CPAl <- df[,c(1:3, 20, 22,24,26)]
CPAli<-df_i[,c(1:3, 21:24)]
Cpal<-rbind(CPAl,CPAli)

```


Correlation matrixes nonlogged 
```{r}


## specific treatments dataframes
C_df <- subset(df_90, treatment == "Tc") # s
S_df <- subset(df_90, treatment == "T1") # s
F_df <- subset(df_90, treatment == "T2") # p
I_df <- subset(df_90, treatment == "T3") # a

## create matrix for correlations by treatment
C_corr_df2 <- rcorr(as.matrix(C_df[, c(4:6,8)])) #
C_corr_df2 # correlation matrix
C_corr_df2$r  # R2 of all correlations
C_corr_df2$P  # P value of all correlations
C_corr_df2$r[C_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

S_corr_df2 <- rcorr(as.matrix(S_df[, c(4:6,8)])) #
S_corr_df2 # correlation matrix
S_corr_df2$r  # R2 of all correlations
S_corr_df2$P  # P value of all correlations
S_corr_df2$r[S_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

F_corr_df2 <- rcorr(as.matrix(F_df[, c(4:6,8)])) #
F_corr_df2 # correlation matrix
F_corr_df2$r  # R2 of all correlations
F_corr_df2$P  # P value of all correlations
F_corr_df2$r[F_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

I_corr_df2 <- rcorr(as.matrix(I_df[, c(4:6,8)])) #
I_corr_df2 # correlation matrix
I_corr_df2$r  # R2 of all correlations
I_corr_df2$P  # P value of all correlations
I_corr_df2$r[I_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

## specific genotypes dataframes
K2_df <- subset(df_90, genotype == "K2") # s
M5_df <- subset(df_90, genotype == "M5") # s
M6_df <- subset(df_90, genotype == "M6") # p

## create matrix for correlations by genotype
K2_corr_df2 <- rcorr(as.matrix(K2_df[, c(4:6,8)])) #
K2_corr_df2 # correlation matrix
K2_corr_df2$r  # R2 of all correlations
K2_corr_df2$P  # P value of all correlations
K2_corr_df2$r[K2_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

M5_corr_df2 <- rcorr(as.matrix(M5_df[, c(4:6,8)])) #
M5_corr_df2 # correlation matrix
M5_corr_df2$r  # R2 of all correlations
M5_corr_df2$P  # P value of all correlations
M5_corr_df2$r[M5_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

M6_corr_df2 <- rcorr(as.matrix(M6_df[, c(4:6,8)])) #
M6_corr_df2 # correlation matrix
M6_corr_df2$r  # R2 of all correlations
M6_corr_df2$P  # P value of all correlations
M6_corr_df2$r[M6_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

```

Correlation MAtrixes for logged data

```{r}
## specific treatments dataframes
C_dfl <- subset(df_90l, treatment == "Tc") # s
S_dfl <- subset(df_90l, treatment == "T1") # s
F_dfl <- subset(df_90l, treatment == "T2") # p
I_dfl <- subset(df_90l, treatment == "T3") # a

## create matrix for correlations by treatment
C_corr_df2l <- rcorr(as.matrix(C_dfl[, c(4, 6:8)])) #
C_corr_df2l # correlation matrix
C_corr_df2l$r  # R2 of all correlations
C_corr_df2l$P  # P value of all correlations
C_corr_df2l$r[C_corr_df2l$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

S_corr_df2l <- rcorr(as.matrix(S_dfl[, c(4, 6:8)])) #
S_corr_df2l # correlation matrix
S_corr_df2l$r  # R2 of all correlations
S_corr_df2l$P  # P value of all correlations
S_corr_df2l$r[S_corr_df2l$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

F_corr_df2l <- rcorr(as.matrix(F_dfl[, c(4, 6:8)])) #
F_corr_df2l # correlation matrix
F_corr_df2l$r  # R2 of all correlations
F_corr_df2l$P  # P value of all correlations
F_corr_df2l$r[F_corr_df2l$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

I_corr_df2l <- rcorr(as.matrix(I_dfl[, c(4, 6:8)])) #
I_corr_df2l # correlation matrix
I_corr_df2l$r  # R2 of all correlations
I_corr_df2l$P  # P value of all correlations
I_corr_df2l$r[I_corr_df2l$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

## specific genotypes dataframes
K2_dfl <- subset(df_90l, genotype == "K2") # s
M5_dfl <- subset(df_90l, genotype == "M5") # s
M6_dfl <- subset(df_90l, genotype == "M6") # p

## create matrix for correlations by genotype
K2_corr_df2l <- rcorr(as.matrix(K2_dfl[, c(4, 6:8)])) #
K2_corr_df2l # correlation matrix
K2_corr_df2l$r  # R2 of all correlations
K2_corr_df2l$P  # P value of all correlations
K2_corr_df2l$r[K2_corr_df2l$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

M5_corr_df2l <- rcorr(as.matrix(M5_dfl[, c(4, 6:8)])) #
M5_corr_df2l # correlation matrix
M5_corr_df2l$r  # R2 of all correlations
M5_corr_df2l$P  # P value of all correlations
M5_corr_df2l$r[M5_corr_df2l$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

M6_corr_df2l <- rcorr(as.matrix(M6_dfl[, c(4, 6:8)])) #
M6_corr_df2l # correlation matrix
M6_corr_df2l$r  # R2 of all correlations
M6_corr_df2l$P  # P value of all correlations
M6_corr_df2l$r[M6_corr_df2l$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)
```

Correlation for Cat for (no inital)
```{r}

df_90
## create matrix for correlations by all
corr_df2 <- rcorr(as.matrix(df_90[, c(4:6,8)])) #
corr_df2 # correlation matrix
corr_df2$r  # R2 of all correlations
corr_df2$P  # P value of all correlations
corr_df2$r[corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)


df_90l
## create matrix for correlations by all logged
corr_df2l <- rcorr(as.matrix(df_90l[, c(4,6:8)])) #
corr_df2l # correlation matrix
corr_df2l$r  # R2 of all correlations
corr_df2l$P  # P value of all correlations
corr_df2l$r[corr_df2l$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

```

```{r}
df_pcal
df_pca

all_corr_df2 <- rcorr(as.matrix(df_pca[, c(4,5,7)])) #
all_corr_df2 # correlation matrix
all_corr_df2$r  # R2 of all correlations
all_corr_df2$P  # P value of all correlations
all_corr_df2$r[all_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

all_corr_dfl2 <- rcorr(as.matrix(df_pcal[, c(4,6,7)])) #
all_corr_dfl2 # correlation matrix
all_corr_dfl2$r  # R2 of all correlations
all_corr_dfl2$P  # P value of all correlations
all_corr_dfl2$r[all_corr_dfl2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

sp_corr_dfl2 <- rcorr(as.matrix(c[, c(4,5,7:8)])) #
sp_corr_dfl2 # correlation matrix
sp_corr_dfl2$r  # R2 of all correlations
sp_corr_dfl2$P  # P value of all correlations
sp_corr_dfl2$r[sp_corr_dfl2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

## specific genotypes dataframes
K2a_df <- subset(df_pca, genotype == "K2") # s
M5a_df <- subset(df_pca, genotype == "M5") # s
M6a_df <- subset(df_pca, genotype == "M6") # p


## create matrix for correlations by genotype
K2a_corr_df2 <- rcorr(as.matrix(K2a_df[, c(4,5,7)])) #
K2a_corr_df2 # correlation matrix
K2a_corr_df2$r  # R2 of all correlations
K2a_corr_df2$P  # P value of all correlations
K2a_corr_df2$r[K2a_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

M5a_corr_df2 <- rcorr(as.matrix(M5a_df[, c(4,5,7)])) #
M5a_corr_df2 # correlation matrix
M5a_corr_df2$r  # R2 of all correlations
M5a_corr_df2$P  # P value of all correlations
M5a_corr_df2$r[M5a_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

M6a_corr_df2 <- rcorr(as.matrix(M6a_df[, c(4,5,7)])) #
M6a_corr_df2 # correlation matrix
M6a_corr_df2$r  # R2 of all correlations
M6a_corr_df2$P  # P value of all correlations
M6a_corr_df2$r[M6a_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

## specific genotypes dataframes
K2a_dfl <- subset(df_pcal, genotype == "K2") # s
M5a_dfl <- subset(df_pcal, genotype == "M5") # s
M6a_dfl <- subset(df_pcal, genotype == "M6") # p

## create matrix for correlations by genotype
K2a_corr_df2l <- rcorr(as.matrix(K2a_dfl[, c(4,6,7)])) #
K2a_corr_df2l # correlation matrix
K2a_corr_df2l$r  # R2 of all correlations
K2a_corr_df2l$P  # P value of all correlations
K2a_corr_df2l$r[K2a_corr_df2l$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

M5a_corr_df2l <- rcorr(as.matrix(M5a_dfl[, c(4,6,7)])) #
M5a_corr_df2l # correlation matrix
M5a_corr_df2l$r  # R2 of all correlations
M5a_corr_df2l$P  # P value of all correlations
M5a_corr_df2l$r[M5a_corr_df2l$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

M6a_corr_df2l <- rcorr(as.matrix(M6a_dfl[, c(4,6,7)])) #
M6a_corr_df2l # correlation matrix
M6a_corr_df2l$r  # R2 of all correlations
M6a_corr_df2l$P  # P value of all correlations
M6a_corr_df2l$r[M6a_corr_df2l$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)
```

Parameters with statistical analyses taken from Acropora Dataclean Ecopys
```{r}
# select columns of interest only
#df_sp <- df[,c(1:3, 19:20, 22, 24, 26)] 
df_sp<-df[,c(1:3, 5,15, 22,24:25)]

data.table::setnames(df_sp, old = c('protein_3d_ug_cm2','chl_ug_cm2', 'logpercent_growth', 'logzoo'), new = c('Pro','Chlo','Growth','Zoox'))
df_sp

## specific treatments dataframes
C_dfsp <- subset(df_sp, treatment == "Tc") # s
S_dfsp <- subset(df_sp, treatment == "T1") # s
F_dfsp <- subset(df_sp, treatment == "T2") # p
I_dfsp <- subset(df_sp, treatment == "T3") # a

## create matrix for correlations by treatment
Csp_corr_df2 <- rcorr(as.matrix(C_dfsp[, c(4, 5,7:8)])) #
Csp_corr_df2 # correlation matrix
Csp_corr_df2$r  # R2 of all correlations
Csp_corr_df2$P  # P value of all correlations
Csp_corr_df2$r[Csp_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

Ssp_corr_df2 <- rcorr(as.matrix(S_dfsp[, c(4, 5,7:8)])) #
Ssp_corr_df2 # correlation matrix
Ssp_corr_df2$r  # R2 of all correlations
Ssp_corr_df2$P  # P value of all correlations
Ssp_corr_df2$r[Ssp_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

Fsp_corr_df2 <- rcorr(as.matrix(F_dfsp[, c(4, 5,7:8)])) #
Fsp_corr_df2 # correlation matrix
Fsp_corr_df2$r  # R2 of all correlations
Fsp_corr_df2$P  # P value of all correlations
Fsp_corr_df2$r[Fsp_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

Isp_corr_df2 <- rcorr(as.matrix(I_dfsp[, c(4, 5,7:8)])) #
Isp_corr_df2 # correlation matrix
Isp_corr_df2$r  # R2 of all correlations
Isp_corr_df2$P  # P value of all correlations
Isp_corr_df2$r[Isp_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

## specific genotypes dataframes
K2sp_df <- subset(df_sp, genotype == "K2") # s
M5sp_df <- subset(df_sp, genotype == "M5") # s
M6sp_df <- subset(df_sp, genotype == "M6") # p

## create matrix for correlations by genotype
K2sp_corr_df2 <- rcorr(as.matrix(K2sp_df[, c(4, 5,7:8)])) #
K2sp_corr_df2 # correlation matrix
K2sp_corr_df2$r  # R2 of all correlations
K2sp_corr_df2$P  # P value of all correlations
K2sp_corr_df2$r[K2sp_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

M5sp_corr_df2 <- rcorr(as.matrix(M5sp_df[, c(4, 5,7:8)])) #
M5sp_corr_df2 # correlation matrix
M5sp_corr_df2$r  # R2 of all correlations
M5sp_corr_df2$P  # P value of all correlations
M5sp_corr_df2$r[M5sp_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

M6sp_corr_df2 <- rcorr(as.matrix(M6sp_df[, c(4, 5,7:8)])) #
M6sp_corr_df2 # correlation matrix
M6sp_corr_df2$r  # R2 of all correlations
M6sp_corr_df2$P  # P value of all correlations
M6sp_corr_df2$r[M6sp_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

```


```{r correlation matrix plot method 1, eval=FALSE, include=FALSE}
### This is the first method of a correlation plot. 
# Control
corrplot(C_corr_df2$r, type="upper", order="hclust", p.mat = C_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
C_corr_plot <- grid.grab()
# Sprinkler
corrplot(S_corr_df2$r, type="upper", order="hclust", p.mat = S_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
S_corr_plot <- grid.grab()
# Feeding
corrplot(F_corr_df2$r, type="upper", order="hclust", p.mat = F_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
F_corr_plot <- grid.grab()
# Interactive
corrplot(I_corr_df2$r, type="upper", order="hclust", p.mat = I_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
I_corr_plot <- grid.grab()
#grid.draw(P1)
plot_grid(C_corr_plot, S_corr_plot,F_corr_plot, I_corr_plot, ncol = 2)
```


```{r}
# K2
corrplot(K2_corr_df2$r, type="upper", order="hclust", p.mat = K2_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
K2_corr_plot <- grid.grab()
# M5
corrplot(M5_corr_df2$r, type="upper", order="hclust", p.mat = M5_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
M5_corr_plot <- grid.grab()
# M6
corrplot(M6_corr_df2$r, type="upper", order="hclust", p.mat = M6_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
M6_corr_plot <- grid.grab()
#grid.draw(P1)
plot_grid(K2_corr_plot, M5_corr_plot, M6_corr_plot, ncol = 1, labels= "AUTO")
```

Correlation plot with logged data
```{r correlation matrix plot method 1, eval=FALSE, include=FALSE}
### This is the first method of a correlation plot. 
# Control
corrplot(C_corr_df2l$r, type="upper", order="hclust", p.mat = C_corr_df2l$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
C_corr_plotl <- grid.grab()
# Sprinkler
corrplot(S_corr_df2l$r, type="upper", order="hclust", p.mat = S_corr_df2l$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
S_corr_plotl <- grid.grab()
# Feeding
corrplot(F_corr_df2l$r, type="upper", order="hclust", p.mat = F_corr_df2l$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
F_corr_plotl <- grid.grab()
# Interactive
corrplot(I_corr_df2l$r, type="upper", order="hclust", p.mat = I_corr_df2l$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
I_corr_plotl <- grid.grab()
#grid.draw(P1)
plot_grid(C_corr_plotl, S_corr_plotl,F_corr_plotl, I_corr_plotl, ncol = 2)
```


```{r}
# K2
corrplot(K2_corr_df2l$r, type="upper", order="hclust", p.mat = K2_corr_df2l$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
K2_corr_plotl <- grid.grab()
# M5
corrplot(M5_corr_df2l$r, type="upper", order="hclust", p.mat = M5_corr_df2l$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
M5_corr_plotl <- grid.grab()
# M6
corrplot(M6_corr_df2l$r, type="upper", order="hclust", p.mat = M6_corr_df2l$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
M6_corr_plotl <- grid.grab()
#grid.draw(P1)
plot_grid(K2_corr_plotl, M5_corr_plotl, M6_corr_plotl, ncol = 1, labels= "AUTO")
```

All treatments (including inital points (n=3))
```{r}
 
corrplot(all_corr_df2$r, type="upper", order="hclust", p.mat = all_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
all_corr_plot <- grid.grab()

corrplot(all_corr_dfl2$r, type="upper", order="hclust", p.mat = all_corr_dfl2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
all_corr_plotl <- grid.grab()
plot_grid(all_corr_plot,all_corr_plotl, ncol = 1, labels= "AUTO")

# K2
corrplot(K2a_corr_df2$r, type="upper", order="hclust", p.mat = K2a_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
K2a_corr_plot <- grid.grab()
# M5
corrplot(M5a_corr_df2$r, type="upper", order="hclust", p.mat = M5a_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
M5a_corr_plot <- grid.grab()
# M6
corrplot(M6a_corr_df2$r, type="upper", order="hclust", p.mat = M6a_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
M6a_corr_plot<- grid.grab()
#grid.draw(P1)
plot_grid(K2a_corr_plot, M5a_corr_plot, M6a_corr_plot, ncol = 1, labels= "AUTO")

#logged
# K2
corrplot(K2a_corr_df2l$r, type="upper", order="hclust", p.mat = K2a_corr_df2l$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
K2a_corr_plotl <- grid.grab()
# M5
corrplot(M5a_corr_df2l$r, type="upper", order="hclust", p.mat = M5a_corr_df2l$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
M5a_corr_plotl <- grid.grab()
# M6
corrplot(M6a_corr_df2l$r, type="upper", order="hclust", p.mat = M6a_corr_df2l$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
M6a_corr_plotl <- grid.grab()
#grid.draw(P1)
plot_grid(K2a_corr_plotl, M5a_corr_plotl, M6a_corr_plotl, ncol = 1, labels= "AUTO")
```


All treatments (with sp data)
```{r}

corrplot(Csp_corr_df2$r, type="upper", order="hclust", p.mat = Csp_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
Csp_corr_plot <- grid.grab()

corrplot(Ssp_corr_df2$r, type="upper", order="hclust", p.mat = Ssp_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
Ssp_corr_plot <- grid.grab()

corrplot(Fsp_corr_df2$r, type="upper", order="hclust", p.mat = Fsp_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
Fsp_corr_plot <- grid.grab()

corrplot(Isp_corr_df2$r, type="upper", order="hclust", p.mat = Isp_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
Isp_corr_plot <- grid.grab()

plot_grid(Csp_corr_plot, Ssp_corr_plot, Fsp_corr_plot, Isp_corr_plot, ncol = 2, labels= "AUTO")

# K2
corrplot(K2sp_corr_df2$r, type="upper", order="hclust", p.mat = K2sp_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
K2sp_corr_plot <- grid.grab()

# M5
corrplot(M5sp_corr_df2$r, type="upper", order="hclust", p.mat = M5sp_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
M5sp_corr_plot <- grid.grab()

# M6
corrplot(M6sp_corr_df2$r, type="upper", order="hclust", p.mat = M6sp_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
M6sp_corr_plot<- grid.grab()

#grid.draw(P1)
plot_grid(K2sp_corr_plot, M5sp_corr_plot, M6sp_corr_plot, ncol = 1, labels= "AUTO")
```


```{r}
#logged
# K2
corrplot(K2a_corr_df2l$r, type="upper", order="hclust", p.mat = K2a_corr_df2l$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
K2a_corr_plotl <- grid.grab()
# M5
corrplot(M5a_corr_df2l$r, type="upper", order="hclust", p.mat = M5a_corr_df2l$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
M5a_corr_plotl <- grid.grab()
# M6
corrplot(M6a_corr_df2l$r, type="upper", order="hclust", p.mat = M6a_corr_df2l$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
M6a_corr_plotl <- grid.grab()
#grid.draw(P1)
plot_grid(K2a_corr_plotl, M5a_corr_plotl, M6a_corr_plotl, ncol = 1, labels= "AUTO")
```

```{r actual correlation matrix plot}
## Final correlation plot (and saving it as PDF)
# Rmarkdown plotting version
par(mfrow=c(2,2))
corrplot.mixed(C_corr_df2$r, upper = "ellipse", p.mat = C_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "Control", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(S_corr_df2$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "Sprinkler", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(F_corr_df2$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "Feeding", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(I_corr_df2$r, upper = "ellipse",  p.mat = I_corr_df2$P,  insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "Interactive", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")
# genotype
corrplot.mixed(K2_corr_df2$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "K2", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M5_corr_df2$r, upper = "ellipse",  p.mat = M5_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "M5", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M6_corr_df2$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "M6", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

#Cat
corrplot.mixed(C_corr_df2$r, upper = "ellipse", p.mat = C_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "Control", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

```


```{r actual correlation matrix plot}
## Final correlation plot (and saving it as PDF)
# Rmarkdown plotting version
par(mfrow=c(2,2))
corrplot.mixed(C_corr_df2l$r, upper = "ellipse", sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "Control", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(S_corr_df2l$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "Sprinkler", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(F_corr_df2l$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "Feeding", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(I_corr_df2l$r, upper = "ellipse",  p.mat = I_corr_df2l$P,  insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "Interactive", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")
# genotype
corrplot.mixed(K2_corr_df2l$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "K2", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M5_corr_df2l$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "M5", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M6_corr_df2l$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "M6", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

```

```{r}
# genotype
corrplot.mixed(K2a_corr_df2$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "K2", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M5a_corr_df2$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "M5", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M6a_corr_df2$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "M6", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

# genotype
corrplot.mixed(K2a_corr_df2l$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "K2", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M5a_corr_df2l$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "M5", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M6a_corr_df2l$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "M6", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

# Cat
corr_df2

corrplot.mixed(corr_df2$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "All", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corr_df2l

corrplot.mixed(corr_df2l$r, upper = "ellipse",  sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.5, title = "All Logged", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")


```


<br/>

**Figure 2.** Correlation matrix for treatments and genotypes depicting pair-wise comparisons of physiological parameters within each treatment and across each genotype Colour and ellipse width denote R^2^ of each significant comparison, and blank grids represent non-significant pair-wise comparisons (*P* > 0.05).Each parameter is denoted in <span style="color: #0072B2;">blue</span> text along the diagonal of each plot. Correlations with R^2^ above 0.5 (shown in <span style="color: #E67D00;">orange</span> and <span style="color: #F21A00;">red</span> in matrix plot) are explored further below.

<br/>

```{r save correlation plot, message=FALSE, warning=FALSE, include=FALSE}
# below saves the figure

par(mfrow=c(2,2))

corrplot.mixed(C_corr_df2$r, upper = "ellipse", number.cex = 0.8, p.mat = C_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title ="Control", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(S_corr_df2$r, upper = "ellipse", number.cex = 0.8, p.mat = S_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "Sprinkler", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(F_corr_df2$r, upper = "ellipse",  number.cex = 0.8, p.mat = F_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "Feeding", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(I_corr_df2$r, upper = "ellipse",  number.cex = 0.8, p.mat = I_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "Interactive", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

#Genotype
corrplot.mixed(K2_corr_df2$r, upper = "ellipse", number.cex = 0.8, p.mat = K2_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "K2", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M5_corr_df2$r, upper = "ellipse",  number.cex = 0.8, p.mat = M5_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "M5", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M6_corr_df2$r, upper = "ellipse",  number.cex = 0.8, p.mat = M6_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "M6", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

### Logged
corrplot.mixed(C_corr_df2l$r, upper = "ellipse", number.cex = 0.8, p.mat = C_corr_df2l$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title ="Control", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(S_corr_df2l$r, upper = "ellipse", number.cex = 0.8, p.mat = S_corr_df2l$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "Sprinkler", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(F_corr_df2l$r, upper = "ellipse",  number.cex = 0.8, p.mat = F_corr_df2l$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "Feeding", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(I_corr_df2l$r, upper = "ellipse",  number.cex = 0.8, p.mat = I_corr_df2l$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "Interactive", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

#Genotype
corrplot.mixed(K2_corr_df2l$r, upper = "ellipse", number.cex = 0.8, p.mat = K2_corr_df2l$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "K2", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M5_corr_df2l$r, upper = "ellipse",  number.cex = 0.8, p.mat = M5_corr_df2l$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "M5", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M6_corr_df2l$r, upper = "ellipse",  number.cex = 0.8, p.mat = M6_corr_df2l$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "M6", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

#Genotype all treat (inital)
corrplot.mixed(K2a_corr_df2$r, upper = "ellipse", number.cex = 0.8, p.mat = K2a_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "K2", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M5a_corr_df2$r, upper = "ellipse",  number.cex = 0.8, p.mat = M5a_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "M5", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M6a_corr_df2$r, upper = "ellipse",  number.cex = 0.8, p.mat = M6a_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "M6", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

#Genotype logged
corrplot.mixed(K2a_corr_df2l$r, upper = "ellipse", number.cex = 0.8, p.mat = K2a_corr_df2l$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "K2", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M5a_corr_df2l$r, upper = "ellipse",  number.cex = 0.8, p.mat = M5a_corr_df2l$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "M5", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M6a_corr_df2l$r, upper = "ellipse",  number.cex = 0.8, p.mat = M6a_corr_df2l$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "M6", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")


corrplot.mixed(corr_df2$r, upper = "ellipse",  number.cex = 0.8, p.mat = corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "All", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(corr_df2l$r, upper = "ellipse",  number.cex = 0.8, p.mat = corr_df2l$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "All Logged", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

### SP parameter data treatment

corrplot.mixed(Csp_corr_df2$r, upper = "ellipse", number.cex = 0.8, p.mat = Csp_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title ="Control", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(Ssp_corr_df2$r, upper = "ellipse", number.cex = 0.8, p.mat = Ssp_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "Sprinkler", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(Fsp_corr_df2$r, upper = "ellipse",  number.cex = 0.8, p.mat = Fsp_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "Feeding", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(Isp_corr_df2$r, upper = "ellipse",  number.cex = 0.8, p.mat = Isp_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "Interactive", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

#Genotype SP
corrplot.mixed(K2sp_corr_df2$r, upper = "ellipse", number.cex = 0.8, p.mat = K2sp_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "K2", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M5sp_corr_df2$r, upper = "ellipse",  number.cex = 0.8, p.mat = M5sp_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "M5", cl.lim = c(-1,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(M6sp_corr_df2$r, upper = "ellipse",  number.cex = 0.8, p.mat = M6sp_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1, title = "M6", cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

```


```{r SSID scatter plots, fig.width = 7, fig.height = 12}
C_df
S_df
F_df
I_df
K2_df
M5_df
M6_df
C_dfl 
S_dfl 
F_dfl 
I_dfl 
K2_dfl
M5_dfl
M6_dfl
df_pca
df_pcal
C_dfsp
S_dfsp
F_dfsp
I_dfsp
K2sp_df
M5sp_df
M6sp_df

C_denVrate <- ggplot(data = df_90, aes(x =treatment , y =Zoox , group = genotype)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab("Treatment") + 
  ylab(dlab) +
  #scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  #scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #\geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  stat_cor(label.y = -0.5, label.x = 3.9) +
  stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()
C_denVrate
```


```{r}
# set up the dataframe
df_subset <- unique(df_subset)# remove any duplicate rows
ldf_subset <- gather(df_subset, param, value, c(4:6, 8))
treat_pca_df <- df_subset[,c(4:6, 8)]

# run the adonis
T_pca_mod <- adonis2(treat_pca_df ~ treatment * genotype, data = df_subset, method = 'eu', permutations = 1000) # below is the model with non sig interactions removed:
#treatment           3   154.68 0.14580 2.9374 0.01998 *
#genotype            2    92.42 0.08712 2.6327 0.07193 .
#treatment:genotype  6   181.88 0.17144 1.7269 0.09990 .
T_pca_mod <- adonis2(treat_pca_df ~ treatment, data = df_subset, by="margin", method = 'eu', permutations = bootnum)
T_pca_mod # view SSID adonis output
#  0.04648 *
# extract pvalues
T_pval <- T_pca_mod["Pr(>F)"]

# perform principal component analysis (PCA)
T_pca <- prcomp(treat_pca_df, center = TRUE, scale= TRUE)
```

```{r SSID PCA plot, fig.height=8, fig.width=8}
# create labels for p values calculated above
T_treat_pval <-substitute(italic(P[treatment])==p, list(p = format(T_pval[1,1], digits = 2)))
#0.041


# Treatment
T_treat_pca <- autoplot(T_pca, data = df_subset, 
         colour = "treatment",
         shape = "treatment",
         fill = "treatment",               
         frame = TRUE, 
         frame.type = "norm",
         frame.alpha = 0.01,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = 1.5, 
         loadings.label.vjust = 0.5,
         loadings.label.repel = TRUE) +
 # scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
  #scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  #scale_fill_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE, override.aes = list(linetype = c(0, 0)))) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = -0.45, y = -0.35, label = deparse(T_treat_pval), parse = TRUE, size = 3)

T_treat_pca
ggsave("T_treat_pca.pdf", width = 10, height = 14, units = "in")
```

```{r}

# set up the dataframe
df_subset <- unique(df_subset)# remove any duplicate rows
ldf_subset <- gather(df_subset, param, value, c(4:6, 8))
geno_pca_df <- df_subset[,c(4:6, 8)]

# run the adonis
I_pca_mod <- adonis2(geno_pca_df ~ treatment * genotype, data = df_subset, method = 'eu', permutations = 1000) # below is the model with non sig interactions removed:
#treatment           3   154.68 0.14580 2.9374 0.02697 *
#genotype            2    92.42 0.08712 2.6327 0.06094 .
#treatment:genotype  6   181.88 0.17144 1.7269 0.07792 .
G_pca_mod <- adonis2(geno_pca_df ~ genotype, data = df_subset, by="margin", method = 'eu', permutations = bootnum)
G_pca_mod # view SSID adonis output
#  0.08796 *
# extract pvalues
G_pval <- G_pca_mod["Pr(>F)"]

# perform principal component analysis (PCA)
G_pca <- prcomp(geno_pca_df, center = TRUE, scale= TRUE)
```

```{r SSID PCA plot, fig.height=8, fig.width=8}
# create labels for p values calculated above
G_geno_pval <-substitute(italic(P[genotype])==p, list(p = format(G_pval[1,1], digits = 2)))
# 0.11


# Treatment
G_geno_pca <- autoplot(G_pca, data = df_subset, 
         colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.alpha = 0.01,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = 1.5, 
         loadings.label.vjust = 0.5,
         loadings.label.repel = TRUE) +
 # scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
  #scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  #scale_fill_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE)) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = -0.45, y = -0.2, label = deparse(G_geno_pval), parse = TRUE, size = 3)

G_geno_pca
ggsave("G_geno_pca.pdf", width = 10, height = 14, units = "in")


C_pca_mod <- adonis2(geno_pca_df ~ cat, data = df_subset, by="margin", method = 'eu', permutations = bootnum)
C_pca_mod # view SSID adonis output
#  0.01649 *  *
# extract pvalues
C_pval <- C_pca_mod["Pr(>F)"]

# perform principal component analysis (PCA)
C_pca <- prcomp(geno_pca_df, center = TRUE, scale= TRUE)
```

```{r SSID PCA plot, fig.height=8, fig.width=8}
# create labels for p values calculated above
C_cat_pval <-substitute(italic(P[cat])==p, list(p = format(C_pval[1,1], digits = 2)))
# 0.014


# Treatment
C_cat_pca <- autoplot(C_pca, data = df_subset, 
         colour = "cat",
         shape = "cat",
         fill = "cat",               
         frame = TRUE, 
         frame.type = "norm",
         frame.alpha = 0.01,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = 1.5, 
         loadings.label.vjust = 0.5,
         loadings.label.repel = TRUE) +
 # scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
  #scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  #scale_fill_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE, override.aes = list(linetype = c(0, 0)))) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = -1, y = -.75, label = deparse(C_cat_pval), parse = TRUE, size = 3)

C_cat_pca

ggsave("C_cat_pca.pdf", width = 10, height = 14, units = "in")

plot_grid(G_geno_pca,C_cat_pca,T_treat_pca)
#########

```

# Genotype difference across treatments (Control)
```{r}
C_df

# set up the dataframe
C_df <- unique(C_df)# remove any duplicate rows
Cldf_subset <- gather(C_df, param, value, c(4:6, 8))
Cg_pca_df <- C_df[,c(4:6, 8)]

# run the adonis
Cg_pca_mod <- adonis2(Cg_pca_df ~  genotype, data = C_df, method = 'eu', permutations = 1000) # below is the model with non sig interactions removed:
#0.5844

# extract pvalues
Cg_pval <- Cg_pca_mod["Pr(>F)"]

# perform principal component analysis (PCA)
Cg_pca <- prcomp(Cg_pca_df, center = TRUE, scale= TRUE)
```


```{r SSID PCA plot, fig.height=8, fig.width=8}
# create labels for p values calculated above
Cg_con_pval <-substitute(italic(P[genotype])==p, list(p = format(Cg_pval[1,1], digits = 2)))
# 0.59


# Treatment
Cg_con_pca <- autoplot(Cg_pca, data = C_df, 
         colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.alpha = 0.01,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = 1.5, 
         loadings.label.vjust = 0.5,
         loadings.label.repel = TRUE) +
 # scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
  #scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  #scale_fill_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE)) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = -1, y = -.75, label = deparse(Cg_con_pval), parse = TRUE, size = 3)

Cg_con_pca

ggsave("Cg_con_pca.pdf", width = 10, height = 14, units = "in")

```


# Genotype difference across treatments (Sprinkler)
```{r}
S_df

# set up the dataframe
S_df <- unique(S_df)# remove any duplicate rows
Sldf_subset <- gather(S_df, param, value, c(4:6, 8))
Sg_pca_df <- S_df[,c(4:6, 8)]

# run the adonis
Sg_pca_mod <- adonis2(Sg_pca_df ~  genotype, data = S_df, method = 'eu', permutations = 1000) # below is the model with non sig interactions removed:
#0.006993

# extract pvalues
Sg_pval <- Sg_pca_mod["Pr(>F)"]

# perform principal component analysis (PCA)
Sg_pca <- prcomp(Sg_pca_df, center = TRUE, scale= TRUE)
```


```{r SSID PCA plot, fig.height=8, fig.width=8}
# create labels for p values calculated above
Sg_spr_pval <-substitute(italic(P[genotype])==p, list(p = format(Sg_pval[1,1], digits = 2)))
# 0.007


#
Sg_spr_pca <- autoplot(Sg_pca, data = S_df, 
         colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.alpha = 0.01,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = 1.5, 
         loadings.label.vjust = 0.5,
         loadings.label.repel = TRUE) +
 # scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
  #scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  #scale_fill_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE)) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = -1, y = -.75, label = deparse(Sg_spr_pval), parse = TRUE, size = 3)

Sg_spr_pca

ggsave("Sg_spr_pca.pdf", width = 10, height = 14, units = "in")

```

# Genotype difference across treatments (Feeding)
```{r}
F_df

# set up the dataframe
F_df <- unique(F_df)# remove any duplicate rows
Fldf_subset <- gather(F_df, param, value, c(4:6, 8))
Fg_pca_df <- F_df[,c(4:6, 8)]

# run the adonis
Fg_pca_mod <- adonis2(Fg_pca_df ~  genotype, data = F_df, method = 'eu', permutations = 1000) # below is the model with non sig interactions removed:
#0.1788

# extract pvalues
Fg_pval <- Fg_pca_mod["Pr(>F)"]

# perform principal component analysis (PCA)
Fg_pca <- prcomp(Fg_pca_df, center = TRUE, scale= TRUE)
```


```{r SSID PCA plot, fig.height=8, fig.width=8}
# create labels for p values calculated above
Fg_fee_pval <-substitute(italic(P[genotype])==p, list(p = format(Fg_pval[1,1], digits = 2)))
# 0.18


#
Fg_fee_pca <- autoplot(Fg_pca, data = F_df, 
         colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.alpha = 0.01,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = 1.5, 
         loadings.label.vjust = 0.5,
         loadings.label.repel = TRUE) +
 # scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
  #scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  #scale_fill_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE)) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = -1, y = -.75, label = deparse(Fg_fee_pval), parse = TRUE, size = 3)

Fg_fee_pca

ggsave("Fg_fee_pca.pdf", width = 10, height = 14, units = "in")

```

# Genotype difference across treatments (Interactive)
```{r}
I_df

# set up the dataframe
I_df <- unique(I_df)# remove any duplicate rows
Ildf_subset <- gather(I_df, param, value, c(4:6, 8))
Ig_pca_df <- I_df[,c(4:6, 8)]

# run the adonis
Ig_pca_mod <- adonis2(Ig_pca_df ~  genotype, data = I_df, method = 'eu', permutations = 1000) # below is the model with non sig interactions removed:
#0.3287

# extract pvalues
Ig_pval <- Ig_pca_mod["Pr(>F)"]

# perform principal component analysis (PCA)
Ig_pca <- prcomp(Ig_pca_df, center = TRUE, scale= TRUE)
```


```{r SSID PCA plot, fig.height=8, fig.width=8}
# create labels for p values calculated above
Ig_int_pval <-substitute(italic(P[genotype])==p, list(p = format(Ig_pval[1,1], digits = 2)))
# 0.33


#
Ig_int_pca <- autoplot(Ig_pca, data = I_df, 
         colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.alpha = 0.01,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = 1.5, 
         loadings.label.vjust = 0.5,
         loadings.label.repel = TRUE) +
 # scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
  #scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  #scale_fill_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE)) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = -1, y = -.75, label = deparse(Ig_int_pval), parse = TRUE, size = 3)

Ig_int_pca

ggsave("Ig_int_pca.pdf", width = 10, height = 14, units = "in")

```

SP data Final PCAs
df_sp

```{r}



# set up the dataframe
df_sp <- unique(df_sp)# remove any duplicate rows
ldf_sp <- gather(df_sp, param, value, c(4:5, 7:8))
treat_pca_dfsp <- df_sp[,c(4:5, 7:8)]

# run the adonis
Tsp_pca_mod <- adonis2(treat_pca_dfsp ~ treatment * genotype, data = df_sp, method = 'eu', permutations = 1000) # below is the model with non sig interactions removed:
#treatment           3    6.576 0.06229 1.0704 0.370629    
#genotype            2   16.762 0.15880 4.0928 0.007992 ***
#treatment:genotype  6    8.501 0.08054 0.6919 0.729271
Tsp_pca_mod <- adonis2(treat_pca_dfsp ~ treatment, data = df_sp, by="margin", method = 'eu', permutations = bootnum)
Tsp_pca_mod # view SSID adonis output
#  0.4254
# extract pvalues
Tsp_pval <- Tsp_pca_mod["Pr(>F)"]

# perform principal component analysis (PCA)
Tsp_pca <- prcomp(treat_pca_dfsp, center = TRUE, scale= TRUE)
```

```{r SSID PCA plot, fig.height=8, fig.width=8}
# create labels for p values calculated above
Tsp_treat_pval <-substitute(italic(P[treatment])==p, list(p = format(Tsp_pval[1,1], digits = 2)))
#0.34


# Treatment
Tsp_treat_pca <- autoplot(Tsp_pca, data = df_sp, 
         colour = "treatment",
         shape = "treatment",
         fill = "treatment",               
         frame = TRUE, 
         frame.type = "norm",
         frame.alpha = 0,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 5, 
         loadings.label.hjust = 1.5, 
         loadings.label.vjust = 0.5,
         loadings.label.repel = TRUE) +
   scale_color_manual(values = c('#66CCFF','#FFFF00', '#FF00CC', '#66FF33'))+
 scale_fill_discrete( labels=c("Sprinkler", "Feeding", "Interactive","Control"))+
 # scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
  #scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  #scale_fill_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE, override.aes = list(linetype = c(0, 0)))) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = -0.45, y = -0.35, label = deparse(Tsp_treat_pval), parse = TRUE, size = 3)

Tsp_treat_pca
ggsave("Tsp_treat_pca.pdf")
```

```{r}

# set up the dataframe
df_sp <- unique(df_sp)# remove any duplicate rows
ldf_sp <- gather(df_sp, param, value, c(4:5, 7:8))
geno_pca_dfsp <- df_sp[,c(4:5, 7:8)]


Gsp_pca_mod <- adonis2(geno_pca_dfsp ~ genotype, data = df_sp, by="margin", method = 'eu', permutations = bootnum)
Gsp_pca_mod # view SSID adonis output
#  0.0064978 *
# extract pvalues
Gsp_pval <- Gsp_pca_mod["Pr(>F)"]

# perform principal component analysis (PCA)
Gsp_pca <- prcomp(geno_pca_dfsp, center = TRUE, scale= TRUE)
```

```{r SSID PCA plot, fig.height=8, fig.width=8}
# create labels for p values calculated above
Gsp_geno_pval <-substitute(italic(P[genotype])==p, list(p = format(Gsp_pval[1,1], digits = 2)))
# 0.0065


# Treatment
Gsp_geno_pca <- autoplot(Gsp_pca, data = df_sp, 
         colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.alpha = 0,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 5, 
         loadings.label.hjust = 1.5, 
         loadings.label.vjust = 0.5,
         loadings.label.repel = TRUE) +
  scale_fill_manual(values = c('red','green4', 'blue'))+
 # scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
  #scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  #scale_fill_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE)) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = -0.4, y = -0.4, label = deparse(Gsp_geno_pval), parse = TRUE, size = 3)

Gsp_geno_pca
ggsave("Gsp_geno_pca.pdf")


Csp_pca_mod <- adonis2(geno_pca_dfsp ~ cat, data = df_sp, by="margin", method = 'eu', permutations = bootnum)
Csp_pca_mod # view SSID adonis output
#   0.1404 *  *
# extract pvalues
Csp_pval <- Csp_pca_mod["Pr(>F)"]

# perform principal component analysis (PCA)
Csp_pca <- prcomp(geno_pca_dfsp, center = TRUE, scale= TRUE)
```

```{r SSID PCA plot, fig.height=8, fig.width=8}
# create labels for p values calculated above
Csp_cat_pval <-substitute(italic(P[cat])==p, list(p = format(Csp_pval[1,1], digits = 2)))
# 0.14


# Interactive
Csp_cat_pca <- autoplot(Csp_pca, data = df_sp, 
         colour = "cat",
         fill = "cat",               
         frame = TRUE, 
         frame.type = "norm",
         frame.alpha = 0,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 5, 
         loadings.label.hjust = -4, 
         loadings.label.vjust = 0.5,
         loadings.label.repel = TRUE) +
 # scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
  #scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  #scale_fill_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE, override.aes = list(linetype = c(0, 0)))) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = -.75, y = -.75, label = deparse(Csp_cat_pval), parse = TRUE, size = 3)

Csp_cat_pca

ggsave("Csp_cat_pca.pdf")

plot_grid(Gsp_geno_pca,Csp_cat_pca,Tsp_treat_pca)
#########

```

# Genotype difference across treatments (Control)
```{r}
C_dfsp

# set up the dataframe
C_dfsp <- unique(C_dfsp)# remove any duplicate rows
Cldf_sp <- gather(C_dfsp, param, value, c(4:5, 7:8))
Cg_pca_dfsp <- C_dfsp[,c(4:5, 7:8)]

# run the adonis
Cspg_pca_mod <- adonis2(Cg_pca_dfsp ~  genotype, data = C_dfsp, method = 'eu', permutations = 1000) # below is the model with non sig interactions removed:
#0.2198

# extract pvalues
Cspg_pval <- Cspg_pca_mod["Pr(>F)"]

# perform principal component analysis (PCA)
Cspg_pca <- prcomp(Cg_pca_dfsp, center = TRUE, scale= TRUE)
```


```{r SSID PCA plot, fig.height=8, fig.width=8}
# create labels for p values calculated above
Cspg_con_pval <-substitute(italic(P[genotype])==p, list(p = format(Cspg_pval[1,1], digits = 2)))
# 0.22


# Treatment
Cspg_con_pca <- autoplot(Cspg_pca, data = C_dfsp, 
         colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.alpha = 0,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 5, 
         loadings.label.hjust = 1.5, 
         loadings.label.vjust =-.5,
         loadings.label.repel = TRUE) +
    scale_fill_manual(values = c('red','green4', 'blue'))+
 # scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
  #scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  #scale_fill_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE)) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = -1, y = -1, label = deparse(Cspg_con_pval), parse = TRUE, size = 3)

Cspg_con_pca

ggsave("Cspg_con_pca.pdf")

```


# Genotype difference across treatments (Sprinkler)
```{r}
S_dfsp

# set up the dataframe
S_dfsp <- unique(S_dfsp)# remove any duplicate rows
Sldf_sp <- gather(S_dfsp, param, value, c(4:5,7:8))
Sg_pca_dfsp <- S_dfsp[,c(4:5,7:8)]

# run the adonis
Sspg_pca_mod <- adonis2(Sg_pca_dfsp ~  genotype, data = S_dfsp, method = 'eu', permutations = 1000)
#0.1109

# extract pvalues
Sspg_pval <- Sspg_pca_mod["Pr(>F)"]

# perform principal component analysis (PCA)
Sspg_pca <- prcomp(Sg_pca_dfsp, center = TRUE, scale= TRUE)
```


```{r SSID PCA plot, fig.height=8, fig.width=8}
# create labels for p values calculated above
Sspg_spr_pval <-substitute(italic(P[genotype])==p, list(p = format(Sspg_pval[1,1], digits = 2)))
# 0.089


#
Sspg_spr_pca <- autoplot(Sspg_pca, data = S_dfsp, 
         colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.alpha = 0,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 5, 
         loadings.label.hjust = 1.5, 
         loadings.label.vjust = 1,
         loadings.label.repel = TRUE) +
      scale_fill_manual(values = c('red','green4', 'blue'))+
 # scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
  #scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  #scale_fill_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE)) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = -1, y = -1.5, label = deparse(Sspg_spr_pval), parse = TRUE, size = 3)

Sspg_spr_pca

ggsave("Sspg_spr_pca.pdf")

```

# Genotype difference across treatments (Feeding)
```{r}
F_dfsp

# set up the dataframe
F_dfsp <- unique(F_dfsp)# remove any duplicate rows
Fldf_sp <- gather(F_dfsp, param, value, c(4:5,7:8))
Fg_pca_dfsp <- F_dfsp[,c(4:5,7:8)]

# run the adonis
Fspg_pca_mod <- adonis2(Fg_pca_dfsp ~  genotype, data = F_dfsp, method = 'eu', permutations = 1000) # below is the model with non sig interactions removed:
#0.3107

# extract pvalues
Fspg_pval <- Fspg_pca_mod["Pr(>F)"]

# perform principal component analysis (PCA)
Fspg_pca <- prcomp(Fg_pca_dfsp, center = TRUE, scale= TRUE)
```


```{r SSID PCA plot, fig.height=8, fig.width=8}
# create labels for p values calculated above
Fspg_fee_pval <-substitute(italic(P[genotype])==p, list(p = format(Fspg_pval[1,1], digits = 2)))
# 0.31


#
Fspg_fee_pca <- autoplot(Fspg_pca, data = F_dfsp, 
         colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.alpha = 0,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 5, 
         loadings.label.hjust = -.5, 
         loadings.label.vjust = .5,
         loadings.label.repel = TRUE) +
        scale_fill_manual(values = c('red','green4', 'blue'))+
 # scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
  #scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  #scale_fill_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE)) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = -1, y = -1.2, label = deparse(Fspg_fee_pval), parse = TRUE, size = 3)

Fspg_fee_pca

ggsave("Fspg_fee_pca.pdf")

```

# Genotype difference across treatments (Interactive)
```{r}
I_dfsp

# set up the dataframe
I_dfsp <- unique(I_dfsp)# remove any duplicate rows
Ildf_sp <- gather(I_dfsp, param, value, c(4:5,7:8))
Ig_pca_dfsp <- I_dfsp[,c(4:5,7:8)]

# run the adonis
Ispg_pca_mod <- adonis2(Ig_pca_dfsp ~  genotype, data = I_dfsp, method = 'eu', permutations = 1000) # below is the model with non sig interactions removed:
#0.3117

# extract pvalues
Ispg_pval <- Ispg_pca_mod["Pr(>F)"]

# perform principal component analysis (PCA)
Ispg_pca <- prcomp(Ig_pca_dfsp, center = TRUE, scale= TRUE)
```


```{r SSID PCA plot, fig.height=8, fig.width=8}
# create labels for p values calculated above
Ispg_int_pval <-substitute(italic(P[genotype])==p, list(p = format(Ispg_pval[1,1], digits = 2)))
# 0.31


#
Ispg_int_pca <- autoplot(Ispg_pca, data = I_dfsp, 
         colour = "genotype",
         shape = "genotype",
         fill = "genotype",               
         frame = TRUE, 
         frame.type = "norm",
         frame.alpha = 0,
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 5, 
         loadings.label.hjust = 1.5, 
         loadings.label.vjust = 0.5,
         loadings.label.repel = TRUE) +
        scale_fill_manual(values = c('red','green4', 'blue'))+
 # scale_shape_manual("treatment", labels = c("Sprinkler", "Feeding", "Interactive", "Control"), values = c("T1","T2","T3","Tc")) +
  #scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  #scale_fill_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
    guides(color = guide_legend(keyheight = 0.3, nrow = 4, byrow = TRUE)) +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.title = element_blank(), legend.background = element_rect(fill = "transparent", colour = NA)) +
  annotate("text", x = -1, y = -1, label = deparse(Ispg_int_pval), parse = TRUE, size = 3)

Ispg_int_pca

ggsave("Ispg_int_pca.pdf")

```



<br/>
Figure:

```{r}
## load the protein bootstrapped model output
df_pro_a <- read.csv("LMER_model_outputs/Protein_model_2021-03-24.csv", head = TRUE)
df_pro_a$ftemp <- as.factor(df_pro_a$ftemp)
df_pro_a$fpco2 <- as.factor(df_pro_a$fpco2)
df_pro_a$species <- factor(df_pro_a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

```


## Supplemental Tables{.tabset} 


```{r protein table}
pro_tab <- df_pro_a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
pro_tab$binder <- paste(pro_tab$species, pro_tab$treat2, sep = "_")
T90_pro_mean <- summarySE(data=pro_tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90_pro_low <- summarySE(data=pro_tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90_pro_up <- summarySE(data=pro_tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))
pro_tab <- cbind(T90_pro_mean, T90_pro_low, T90_pro_up)[, c(1,2,4,5,13,21)]
pro_tab$mean <- round(pro_tab$mean, 2)
pro_tab$lowerci <- round(pro_tab$lowerci, 2)
pro_tab$upperci <- round(pro_tab$upperci, 2)
colnames(pro_tab)[colnames(pro_tab)=="treat2"] <- "treatment"
colnames(pro_tab)[colnames(pro_tab)=="lowerci"] <- "lower 95%"
colnames(pro_tab)[colnames(pro_tab)=="upperci"] <- "upper 95%"
pro_tab$treatment <- factor(pro_tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))
table1 <- kable(pro_tab[,-c(1)], booktabs = T, caption = "Table 1. T90 modeled mean coral host protein content and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 8) %>%
  pack_rows("(b) PSTR", 9, 16) %>%
  pack_rows("(c) PAST", 17, 24)
table1
```

```{r lipid table}
lipid_tab <- df_lipid_a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
lipid_tab$binder <- paste(lipid_tab$species, lipid_tab$treat2, sep = "_")
T90_lipid_mean <- summarySE(data=lipid_tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90_lipid_low <- summarySE(data=lipid_tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90_lipid_up <- summarySE(data=lipid_tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))
lipid_tab <- cbind(T90_lipid_mean, T90_lipid_low, T90_lipid_up)[, c(1,2,4,5,13,21)]
lipid_tab$mean <- round(lipid_tab$mean, 2)
lipid_tab$lowerci <- round(lipid_tab$lowerci, 2)
lipid_tab$upperci <- round(lipid_tab$upperci, 2)
colnames(lipid_tab)[colnames(lipid_tab)=="treat2"] <- "treatment"
colnames(lipid_tab)[colnames(lipid_tab)=="lowerci"] <- "lower 95%"
colnames(lipid_tab)[colnames(lipid_tab)=="upperci"] <- "upper 95%"
lipid_tab$treatment <- factor(lipid_tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))
table2 <- kable(lipid_tab[,-c(1)], booktabs = T, caption = "Table 2. T90 modeled mean coral host lipid content and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 8) %>%
  pack_rows("(b) PSTR", 9, 16) %>%
  pack_rows("(c) PAST", 17, 24)
table2
```

```{r carbohydrate table}
carb_tab <- df_carb_a[,c(9,15,18:20)] #subset for species, treatment, and model values
carb_tab$binder <- paste(carb_tab$species, carb_tab$treat2, sep = "_")
T90_carb_mean <- summarySE(data=carb_tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90_carb_low <- summarySE(data=carb_tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90_carb_up <- summarySE(data=carb_tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))
carb_tab <- cbind(T90_carb_mean, T90_carb_low, T90_carb_up)[, c(1,2,4,5,13,21)]
carb_tab$mean <- round(carb_tab$mean, 2)
carb_tab$lowerci <- round(carb_tab$lowerci, 2)
carb_tab$upperci <- round(carb_tab$upperci, 2)
colnames(carb_tab)[colnames(carb_tab)=="treat2"] <- "treatment"
colnames(carb_tab)[colnames(carb_tab)=="lowerci"] <- "lower 95%"
colnames(carb_tab)[colnames(carb_tab)=="upperci"] <- "upper 95%"
carb_tab$treatment <- factor(carb_tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))
table3 <- kable(carb_tab[,-c(1)], booktabs = T, caption = "Table 3. T90 modeled mean coral host carbohydrate content and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 8) %>%
  pack_rows("(b) PSTR", 9, 16) %>%
  pack_rows("(c) PAST", 17, 24)
table3
```

```{r density table}
den_tab <- df_den_a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
den_tab$binder <- paste(den_tab$species, den_tab$treat2, sep = "_")
T90_den_mean <- summarySE(data=den_tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90_den_low <- summarySE(data=den_tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90_den_up <- summarySE(data=den_tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))
den_tab <- cbind(T90_den_mean, T90_den_low, T90_den_up)[, c(1,2,4,5,13,21)]
den_tab$mean <- round(den_tab$mean, 2)
den_tab$lowerci <- round(den_tab$lowerci, 2)
den_tab$upperci <- round(den_tab$upperci, 2)
colnames(den_tab)[colnames(den_tab)=="treat2"] <- "treatment"
colnames(den_tab)[colnames(den_tab)=="lowerci"] <- "lower 95%"
colnames(den_tab)[colnames(den_tab)=="upperci"] <- "upper 95%"
den_tab$treatment <- factor(den_tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))
table4 <- kable(den_tab[,-c(1)], booktabs = T, caption = "Table 4. T90 modeled mean algal endosymbiont cell density and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 8) %>%
  pack_rows("(b) PSTR", 9, 16) %>%
  pack_rows("(c) PAST", 17, 24)
table4
```

```{r chlorophyll table}
chla_tab <- df_chla_a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
chla_tab$binder <- paste(chla_tab$species, chla_tab$treat2, sep = "_")
T90_chla_mean <- summarySE(data=chla_tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90_chla_low <- summarySE(data=chla_tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90_chla_up <- summarySE(data=chla_tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))
chla_tab <- cbind(T90_chla_mean, T90_chla_low, T90_chla_up)[, c(1,2,4,5,13,21)]
chla_tab$mean <- round(chla_tab$mean, 2)
chla_tab$lowerci <- round(chla_tab$lowerci, 2)
chla_tab$upperci <- round(chla_tab$upperci, 2)
colnames(chla_tab)[colnames(chla_tab)=="treat2"] <- "treatment"
colnames(chla_tab)[colnames(chla_tab)=="lowerci"] <- "lower 95%"
colnames(chla_tab)[colnames(chla_tab)=="upperci"] <- "upper 95%"
chla_tab$treatment <- factor(chla_tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))
table5 <- kable(chla_tab[,-c(1)], booktabs = T, caption = "Table 5. T90 modeled mean algal endosymbiont chlorophyll a content and 95% confichlace intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 8) %>%
  pack_rows("(b) PSTR", 9, 16) %>%
  pack_rows("(c) PAST", 17, 24)
table5
```

```{r host table}
host_tab <- df_host_a[,c(9,15,16,18:20)] #subset for species, treatment, parameter, and model values
host_tab$binder <- paste(host_tab$species, host_tab$param, host_tab$treat2, sep = "_")
T90_host_mean <- summarySE(data=host_tab, measurevar = "mean", groupvars = c("species", "param", "treat2", "binder"))
T90_host_low <- summarySE(data=host_tab, measurevar = "lowerci", groupvars = c("species", "param", "treat2", "binder"))
T90_host_up <- summarySE(data=host_tab, measurevar = "upperci", groupvars = c("species", "param", "treat2", "binder"))
host_tab <- cbind(T90_host_mean, T90_host_low, T90_host_up)[, c(1,3,5,6,15,24)]
host_tab$mean <- round(host_tab$mean, 2)
host_tab$lowerci <- round(host_tab$lowerci, 2)
host_tab$upperci <- round(host_tab$upperci, 2)
colnames(host_tab)[colnames(host_tab)=="treat2"] <- "treatment"
colnames(host_tab)[colnames(host_tab)=="lowerci"] <- "lower 95%"
colnames(host_tab)[colnames(host_tab)=="upperci"] <- "upper 95%"
host_tab$treatment <- factor(host_tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))
table6 <- kable(host_tab[,-c(1)], booktabs = T, caption = "Table 6. Total coral host physiology at T90 modeled mean and 95% confidence intervals for each physiological parameter per species ") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 8) %>%
  pack_rows("(b) PSTR", 9, 16) %>%
  pack_rows("(c) PAST", 17, 24)
table6
```


```{r excel WB, message=FALSE, warning=FALSE}
### Create workbook
wb <- createWorkbook()
# add 'Table 1' worksheet
addWorksheet(wb, "Table 1 - protein") 
writeData(wb, sheet = 1, x = pro_tab)
setColWidths(wb, sheet = 1, cols = 1:5, widths = "auto")
# add 'Table 2' worksheet
addWorksheet(wb, "Table 2 - lipid") 
writeData(wb, sheet = 2, x = lipid_tab)
setColWidths(wb, sheet = 2, cols = 1:5, widths = "auto")
# add 'Table 3' worksheet
addWorksheet(wb, "Table 3 - carbohydrate") 
writeData(wb, sheet = 3, x = carb_tab)
setColWidths(wb, sheet = 3, cols = 1:5, widths = "auto")
# add 'Table 4' worksheet
addWorksheet(wb, "Table 4 - density") 
writeData(wb, sheet = 4, x = den_tab)
setColWidths(wb, sheet = 4, cols = 1:5, widths = "auto")
# add 'Table 5' worksheet
addWorksheet(wb, "Table 5 - chlorophyll") 
writeData(wb, sheet = 5, x = chla_tab)
setColWidths(wb, sheet = 5, cols = 1:5, widths = "auto")
# add 'Table 6' worksheet
addWorksheet(wb, "Table 6 - total host") 
writeData(wb, sheet = 6, x = host_tab)
setColWidths(wb, sheet = 6, cols = 1:5, widths = "auto")
# save workbook
saveWorkbook(wb, file="Data/Supplemental/Supplemental_Tables.xlsx", overwrite = TRUE)
```



<br/>


## Session information

Session information from the last run date on `r date`:

```{r}
sessionInfo()
```

